---
title: "Groundfish Framework 65 --herring and mackerel"
author: "Min-Yang Lee"
date: "3/7/2022"
output:
  pdf_document: default
  html_document: default
urlcolor: blue

---

<!---
In order to do a data update, you need all of the params set to "live". It takes a long, long time. --->
# Project setup
here(), load libraries, and set a data vintage.  


```{r setup, include=TRUE, echo=TRUE, results=FALSE}
# Set Path
here::i_am("GF65_herring_mackerel/data_wrangle/data_extracting.rmd")

# Please ensure you have the proper packages installed with (install.packages()) or a request to ITD if any libaries do not load.  
library("here")
library("RODBC")
library("tibble")
library("dplyr")
library("haven")
library("lubridate")
library("readr")
vintage_string<-Sys.Date()
vintage_string<-gsub("-","_",vintage_string)


START.YEAR = 2019
END.YEAR = 2021

# Credentials
source(here("R_code","project_logistics","R_credentials_RODBC.R"))
# This file leaves behind the following things:
# oracle_username
# oracle_server
# oracle_password

# Set up paths.
herring_haddock_AM_location<-here("input_data","Herring_Haddock_Accountability_Measure_Areas")
```

# Organization


```{r folder_create, include=TRUE, echo=FALSE, results=FALSE}
# You only need to run this once, but nothing bad will happen if you keep include=TRUE.

# Set up some folders

dir.create(here("GF65_herring_mackerel","data"), showWarnings="FALSE")
dir.create(here("GF65_herring_mackerel","data", "intermediate"), showWarnings="FALSE")
dir.create(here("GF65_herring_mackerel","data", "main"), showWarnings="FALSE")

```

# Purpose

This code extracts and processes data.  We will produce a dataset containing:

*    Permit (no need to filter by LA or open access herring/mackerel vessels)
*    NESPP3 (herring and mackerel only)
*    Year (2019-2021 or 2020-2022 if data is complete)
*    Month
*    Landings
*    Revenue
*    Area, where area comes from the shapoefile found at herring_haddock_AM 

# Dependencies

This code depends on:

1.  Network access to get the APSD_DMIS_2.rda and trip cost data from places on the NEFSC network.
1.  The ability to connect to NEFSC oracle databases (VTR and the Live DMIS tables at ``APSD.t_ssb_trip_current@garfo_nefsc``).


# Data Overview
##  DMIS
We are using the APSD.t_ssb_catch_current and APSD.t_ssb_trip_current tables. We're only using the APSD.t_ssb_trip_current as a conveient way to pull out the calendar_year and trip_date fields, so we can categorize by month. We use statistical area (AREA) to assign to the haddock AM areas.   See the DMIS documentation for further information. 


# Loading Data fom Oracle 

I'm using DMIS to get the broad stock area (area) and the herring and SMB permits for trips that caught herring or mackerel.

```{r DMIS_Query, echo=TRUE,eval=TRUE}
oracle_server = "sole"

  ODBC.CONNECTION <- RODBC::odbcConnect(dsn=oracle_server, uid=oracle_username, pwd=oracle_password, believeNRows=FALSE)

CURRENT.QUERY <- paste("select t.trip_date, t.calendar_year, c.* from APSD.t_ssb_catch_current@garfo_nefsc  c, APSD.t_ssb_trip_current@garfo_nefsc t
where c.NESPP3 in (168, 212)
and c.trip_id=t.trip_id 
and t.calendar_year between", START.YEAR, "and",END.YEAR, sep=" ")
DMIS_DATA = sqlQuery(ODBC.CONNECTION, CURRENT.QUERY)

odbcCloseAll()



#save to RDS
DMIS_DATA_name <-paste0("DMIS_extra_data",vintage_string,".Rds")
saveRDS(DMIS_DATA, file=here("GF65_herring_mackerel", "data","intermediate",DMIS_DATA_name))
```


# Tidying up

Send the NAs to zeros and bin into Haddock AM areas.

```{r merge, include=TRUE, echo=TRUE, results=TRUE, eval=TRUE}
#final_product<-dplyr::left_join(APSD.DMIS_WIND_TEST, DMIS_DATA, by = c("DOCID" = "DOCID"))

final_product<-DMIS_DATA
#Remove NAs from 2 of the value columns. Set them to zero.
final_product<-final_product%>%
    dplyr::mutate(DLR_DOLLAR=ifelse(is.na(DLR_DOLLAR),0,DLR_DOLLAR),
                 DOLLAR_SSB=ifelse(is.na(DOLLAR_SSB),0,DOLLAR_SSB)
                 )


#assign by Stat area
# 513, 514, 515 -- GOM Area
# 521, 522, 561, 562, 525 GB area
final_product$Area_by_stat<-"NONE"
final_product$Area_by_stat[final_product$AREA==513]<-"GOM_AREA"
final_product$Area_by_stat[final_product$AREA==514]<-"GOM_AREA"
final_product$Area_by_stat[final_product$AREA==515]<-"GOM_AREA"

final_product$Area_by_stat[final_product$AREA==521]<-"GB_AREA"
final_product$Area_by_stat[final_product$AREA==522]<-"GB_AREA"
final_product$Area_by_stat[final_product$AREA==561]<-"GB_AREA"
final_product$Area_by_stat[final_product$AREA==562]<-"GB_AREA"
final_product$Area_by_stat[final_product$AREA==525]<-"GB_AREA"

final_product$Month<-lubridate::month(final_product$TRIP_DATE)

#Summary
final_product %>%
  group_by(Area_by_stat, CALENDAR_YEAR) %>%
  summarise(pounds=sum(POUNDS), landed=sum(LANDED), revenue=sum(DLR_DOLLAR)) %>%
  ungroup





final_DATA_name <-paste0("herring_data",vintage_string)
saveRDS(final_product, file=here("GF65_herring_mackerel", "data","main",paste0(final_DATA_name,".Rds")))
haven::write_sas(data=final_product, path=here("GF65_herring_mackerel", "data","main",paste0(final_DATA_name,".sas7bdat")))

write_delim(final_product, 
            file=here("GF65_herring_mackerel","data","main",paste0(final_DATA_name,".csv")),
            delim=",")



```


# R Session Information
```{r session_info, include=TRUE, echo=TRUE, results=TRUE, eval=TRUE}
sessionInfo()
Sys.Date()

```
This may be useful for diagnosing and troubleshooting one day.


