---
title: "Groundfish Framework 65 --herring and mackerel"
author: "Min-Yang Lee"
date: "3/7/2022"
output:
  pdf_document: default
  html_document: default
urlcolor: blue

---

<!---
In order to do a data update, you need all of the params set to "live". It takes a long, long time. --->
# Project setup
here(), load libraries, and set a data vintage.  


```{r setup, include=TRUE, echo=TRUE, results=FALSE}
# Set Path
here::i_am("GF65_herring_mackerel/data_wrangle/data_extracting.rmd")

# Please ensure you have the proper packages installed with (install.packages()) or a request to ITD if any libaries do not load.  
library("here")
library("RODBC")
library("tibble")
library("dplyr")
library("lubridate")
vintage_string<-Sys.Date()
vintage_string<-gsub("-","_",vintage_string)


START.YEAR = 2019
END.YEAR = 2021

# Credentials
source(here("R_code","project_logistics","R_credentials_RODBC.R"))
# This file leaves behind the following things:
# oracle_username
# oracle_server
# oracle_password

# Set up paths.
herring_haddock_AM_location<-here("input_data","Herring_Haddock_Accountability_Measure_Areas")
```

# Organization


```{r folder_create, include=TRUE, echo=FALSE, results=FALSE}
# You only need to run this once, but nothing bad will happen if you keep include=TRUE.

# Set up some folders

dir.create(here("GF65_herring_mackerel","data"), showWarnings="FALSE")
dir.create(here("GF65_herring_mackerel","data", "intermediate"), showWarnings="FALSE")
dir.create(here("GF65_herring_mackerel","data", "main"), showWarnings="FALSE")

```

# Purpose

This code extracts and processes data.  We will produce a dataset containing:

*    Permit (no need to filter by LA or open access herring/mackerel vessels)
*    NESPP3 (herring and mackerel only)
*    Year (2019-2021 or 2020-2022 if data is complete)
*    Month
*    Landings
*    Revenue
*    Area, where area comes from the shapoefile found at herring_haddock_AM 

# Dependencies

This code depends on:

1.  Network access to get the APSD_DMIS_2.rda and trip cost data from places on the NEFSC network.
1.  The ability to connect to NEFSC oracle databases (VTR and the Live DMIS tables at ``APSD.t_ssb_trip_current@garfo_nefsc``).


# Data Overview
##  DMIS
We are using the DMIS_APSD_2 table.  This is a custom data query that combines [DMIS](https://github.com/NEFSC/READ-SSB-Lee-metadata/blob/master/DMIS.md) and SFCLAM data and was constructed to support the [Wind Energy tool](https://github.com/dcorvi/offshoreWind).  The sql code can be found [here](https://github.com/NEFSC/READ-SSB-Lee-metadata/blob/master/external/MAKE_DMIS_SFCLAM_122121.sql) and [here](https://github.com/NEFSC/READ-SSB-Lee-metadata/blob/master/external/make_sfclam_only_013022.sql). 
```{r APSD_DMIS_2 overview, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
| Column  | Description           |
|------------|:-----------------------------------------------|
|DOCID | VTR DOCUMENT table record identifier; Primary key, internally generated at scanning based on vessel id and date/time sailed. Each DOCID represents one trip; equivalent to TRIPID in VESLOGyyyyT,S,G tables.  There is no DOCID in older SFCLAM data.|
|IMGID |VTR IMAGES table primary key; generated internally at scanning. Each IMGID represents one scanned VTR document. Foreign key linking to VTR CATCH table.  Equivalent to the GEARID in VTR.VESLOGyyyyG |
|SECGEARFISH |A three digit code for the gear used  |
|GEARCODE |A description of the gears used. This has constructed by aggregating SECGEARFISH |
|SPPNAME | Common name of the species.|
|NESPP3 |Three digit code used to identify the species |
|SOURCE | ==DMIS or ==SFCLAM |
|Dates | VTR land date, AMS Land Date, Dealer Sold Date Trip date is broken down into fields Calendar_Year, Month_of_Year, Week_of_Year, and Day_of_Year|
|DDLAT | Latitude in decimal degrees| 
|DDLON  | Longitude in decimal degrees| 
|PERMIT | Six-digit vessel fishing permit number assigned by the NE Regional Office permit system|
|DOLLAR | This is the nominal value of fish sold.An imputed price is used in cases where the value was not reported.|
|POUNDS | POUNDS is live weight|
|LANDED |  LANDED whatever was landed, in whatever form it was landed|
|TRIP_LENGTH | Trip length is in days; It is calculated from the elapsed time between the date-time sailed and date-time landed. This is a measure of days absent.|
"
cat(tabl) 
```

```{r DMIS_extra overview, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
| Column  | Description           |
|------------|:-----------------------------------------------|
| TRIP_ID| Don't use this column except for making a DMIS to DMIS join. |
| DAS_ID| Identifier to link to AMS data.|
|DOCID | VTR DOCUMENT table record identifier; Primary key, internally generated at scanning based on vessel id and date/time sailed. Each DOCID represents one trip; equivalent to TRIPID in VESLOG tables.|
|ACTIVITY_CODE| Complicated set of letters and numbers. See below|
| PLAN_CAT | HRG_A through HRG_D and SMB_1 through SMB_5 are a collection of true and false variables the indicate if the vessel had a particular permit when the trip was taken.  The DMIS data is missing some HRG categories.|
"
cat(tabl) 
```

ACTIVITY_CODE and a set of PLAN_CAT categorical variables are used from the live DMIS tables. We join using DOCID.

A little more information about [VTR](https://github.com/NEFSC/READ-SSB-Lee-metadata/blob/master/veslog.md).

*  It's possible that the previous trip was the same day.  It's also possible that the previous trip was from years before.  
*The date that I am using here is the `datelnd1` field from VESLOG_T, if those are somehow missing, I have used datesold from VESLOG_S. I am using something from the Clam logbooks, but I'm not positive as to what. I normally used the datesold in VESLOG_S for spacepanels.  

*  More of the `previous_` variables are missing. This is expected, because the first observation of a permit will be missing something. I don't think this will cause too much of a problem.  Some will be missing if the prior trip was a "other state."

# Load Offshore Wind Tool Data sets 

The frozen DMIS table from the offshoreWind project (APSD_DMIS_2) is the base dataset for the analysis.  The DMIS data are formed by combining many datasets, including VTR and Dealer.  In brief, the APSD_DMIS_2 dataset contains a mix of trip attributes (port, date),  sub-trip attributes (gear, location) , and catch outcomes (species, pounds, landed, dollar).  You can read more about DMIS [here](https://github.com/NEFSC/READ-SSB-Lee-metadata/blob/master/DMIS.md).


```{r Data Set Loading, echo=TRUE, results=FALSE,eval=TRUE}
# Do a live data query on DMIS OR 

  oracle_server = "sole"
  ODBC.CONNECTION <- RODBC::odbcConnect(dsn=oracle_server, uid=oracle_username, pwd=oracle_password, believeNRows=FALSE)
  CURRENT.QUERY <- paste ("select * FROM APSD.DMIS_WIND_TEST@garfo_nefsc
   WHERE (YEAR BETWEEN",START.YEAR,"AND",END.YEAR,")", 
   "AND NESPP3 IN ('168','212')", sep=" ")
  APSD.DMIS_WIND_TEST = sqlQuery(ODBC.CONNECTION, CURRENT.QUERY)
  odbcCloseAll()
  
  APSD.DMIS_WIND_TEST$dbsource<-paste0("live_",vintage_string)

Wind_dataname <-paste0("DMIS_WIND_TEST",vintage_string,".Rds")
saveRDS(APSD.DMIS_WIND_TEST, file=here("GF65_herring_mackerel", "data","intermediate",Wind_dataname))



##### copy over a frozen DMIS table from a location on the network.

# Pick the most recent APSD_DMIS2 file. 
```


This match should be pretty good for source=DMIS. But it will not work for source=SFCLAM.

# Loading Data fom Oracle 

The APSD_DMIS_2 table must be supplemented with additional data.  This section queries the Oracle databases to extract additional information.



## Herring Permit and BROAD_STOCK AREA  

I'm using DMIS to get the broad stock area (BROAD_AREA) and the herring and SMB permits for trips that caught herring or mackerel.

```{r DMIS_Query, echo=TRUE,eval=TRUE}
oracle_server = "sole"

  ODBC.CONNECTION <- RODBC::odbcConnect(dsn=oracle_server, uid=oracle_username, pwd=oracle_password, believeNRows=FALSE)

CURRENT.QUERY <- paste ("SELECT TRIP_ID, DOCID, ACTIVITY_CODE, BROAD_AREA,HRG_A, HRG_B, HRG_C, HRG_D, SMB_1, SMB_2, SMB_3, SMB_4, SMB_5
 FROM APSD.t_ssb_trip_current@garfo_nefsc 
 WHERE TRIP_ID in 
    (select distinct TRIP_ID FROM APSD.t_ssb_catch_current@garfo_nefsc 
        where NESPP3 in (168, 212)
    ) AND
 (CALENDAR_YEAR BETWEEN",START.YEAR,"AND",END.YEAR,")", sep=" ")
DMIS_DATA = sqlQuery(ODBC.CONNECTION, CURRENT.QUERY)

odbcCloseAll()



#save to RDS
DMIS_DATA_name <-paste0("DMIS_extra_data",vintage_string,".Rds")
saveRDS(DMIS_DATA, file=here("GF65_herring_mackerel", "data","intermediate",DMIS_DATA_name))
```


# Joins
Join the wind dataset to the supplementary DMIS dataset, on TRIP_ID. Keep rows that are in the APSD.DMIS_WIND_TEST dataset.  Assign the GB and GOM areas based on the broad stock area in DMIS.

```{r merge, include=TRUE, echo=TRUE, results=TRUE, eval=TRUE}
final_product<-dplyr::left_join(APSD.DMIS_WIND_TEST, DMIS_DATA, by = c("DOCID" = "DOCID"))

#assign by Stat area
# 513, 514, 515 -- GOM Area
# 521, 522, 561, 562, 525 GB area
final_product$Area_by_stat<-"NONE"
final_product$Area_by_stat[final_product$BROAD_AREA==513]<-"GOM_AREA"
final_product$Area_by_stat[final_product$BROAD_AREA==514]<-"GOM_AREA"
final_product$Area_by_stat[final_product$BROAD_AREA==515]<-"GOM_AREA"

final_product$Area_by_stat[final_product$BROAD_AREA==521]<-"GB_AREA"
final_product$Area_by_stat[final_product$BROAD_AREA==522]<-"GB_AREA"
final_product$Area_by_stat[final_product$BROAD_AREA==561]<-"GB_AREA"
final_product$Area_by_stat[final_product$BROAD_AREA==562]<-"GB_AREA"
final_product$Area_by_stat[final_product$BROAD_AREA==525]<-"GB_AREA"


final_product <- final_product$Month<-lubridate::month(final_product$DATE_TRIP)


final_DATA_name <-paste0("herring_data",vintage_string,".Rds")
saveRDS(final_product, file=here("GF65_herring_mackerel", "data","main",final_DATA_name))
```


# R Session Information
```{r session_info, include=TRUE, echo=TRUE, results=TRUE, eval=TRUE}
sessionInfo()
Sys.Date()

```
This may be useful for diagnosing and troubleshooting one day.


