---
title: "SIR 2025-2027 Specifications Economic Section"
author: "Min-Yang Lee"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    number_sections: yes
  word_document: default
  html_document:
    df_print: paged
header-includes: \usepackage{setspace}\doublespacing
urlcolor: blue
editor_options:
  chunk_output_type: console
fontsize: 12pt
---

# Summary and Housekeeping
The 2025-2027 Atlantic herring fishery specifications are needed to set the ABCs, ACLs, and other specifications. This is an application of the ABC control rule established with Amendment 8. The previous specifications were set in Framework Adjustment 8 (FW8) and a specifications action for 2023-2025.

A supplemental information report (SIR) is being prepared for these specifications. *If* there are no implementing regulations, then only a Regulatory Flexibility Act Analysis is required. In this action, there is an implementing regulation (New Brunswick Weir), therefore an EO 12866 section is required.

This analysis was written in RMarkdown. It can be found at https://github.com/NEFSC/READ-SSB-Lee-regulatory-analyses

\clearpage

 <!---- 
 The global_options chunk loads libraries, sets options, figures out if you're on a desktop or server, sets years, and sets graphing options
 --->
```{r global_options, include=FALSE}

 library("data.table")
 library("scales")
 library("ggplot2")
 library("dplyr")
 library("tidyr")
 library("stringr")
 library("knitr")
 library("lubridate")
 library("here")
 library("kableExtra")
 library("haven")
here::i_am("writing/SIR2025_Economic_Impacts.Rmd")

#############################################################################
#knitr options

knitr::opts_chunk$set(echo=FALSE, warning = FALSE, error = FALSE, message = FALSE, comment = FALSE, cache = FALSE, progress = TRUE, verbose = FALSE, 
											dpi = 600)
options(tinytex.verbose = TRUE)
# options(knitr.table.format = "latex")
#############################################################################


# RFA data
RFA_filepath<-file.path("//nefscdata","RFA_EO12866_Guidelines" ,"Ownership Data", "current data and metadata","affiliates_2024_06_01.Rdata")

# DeflatorsY, which are pulled by stata
# DeflatorsQ, which are pulled by stata

deflatorsY_path<-here("data_folder","external" ,"deflatorsY.dta")
deflatorsQ_path<-here("data_folder","external" ,"deflatorsQ.dta")

monthly_util_herring_path<-here("data_folder","intermediate" ,"monthly_util_herring.dta")


###################################################################################################
```

```{r Set_switches, eval=TRUE}
# Data_Process_Switch<-TRUE will extract and process data. This takes a while, so set to FALSE after you run the first time.
#Data_Process_Switch<-FALSE
#source(here("R_code","project_logistics","R_credentials_RODBC.R"))

```	


```{r Get_Deflators, include=FALSE, eval=TRUE}


#import deflators this with haven.
deflatorsY<-haven::read_dta(file=deflatorsY_path)%>%
  select(year,fGDPDEF_2023) %>%
  filter(year<=2023)
deflatorsQ<-haven::read_dta(file=deflatorsQ_path)%>%
  select(dateq,fGDPDEF_2023Q1)

monthly_util_herring<-haven::read_dta(file=monthly_util_herring_path)


```

```{r load_RFA_data, include=FALSE}
load(RFA_filepath)
affiliates<-affiliates_2024_06_01
rm(affiliates_2024_06_01)

```





<!--- Set the figure numbers for the section, subsection, figures, and tables so things are properly numbered--->


\setcounter{section}{8}
\setcounter{subsection}{11}

\setcounter{figure}{15}
\setcounter{table}{12}



## Regulatory Impact Analysis 

The purpose of Executive Order 12866 (E.O. 12866, 58 FR 51735, October 4, 1993), as amended by E.O. 14094 (88 FR 21879, April 6, 2023) is to enhance planning and coordination with respect to new and
existing regulations. 
This E.O. requires the Office of Management and Budget (OMB) to review regulatory programs that are considered to be “significant.” 
A significant action is any regulatory action that may:

1. Have an annual effect on the economy of $200 million or more (adjusted every 3 years by the Administrator of the Office of Information and Regulatory Affairs (OIRA)  for changes in gross domestic product); or adversely affect in a material way the economy, a sector of the economy, productivity, competition, jobs, the environment, public health or safety, or State, local, territorial, or tribal governments or communities;

2. Create a serious inconsistency or otherwise interfere with an action taken or planned by another agency;

3. Materially alter the budgetary impact of entitlements, grants, user fees, or loan programs or the rights and obligations of recipients thereof; or

4. Raise legal or policy issues for which centralized review would meaningfully further the President's priorities or the principles set forth in this Executive order, as specifically authorized in a timely manner by the Administrator of OIRA in each case.

In deciding whether and how to regulate, agencies should assess all costs and benefits of available regulatory alternatives. Costs and benefits shall be understood to include both quantifiable measures (to the fullest extent that these can be usefully estimated) and qualitative measures of costs and benefits that are difficult to quantify, but nevertheless essential to consider. 

The draft action will set ACLs and other fishery specification for 2025-2027. In aggregate these changes will allow the fishing industry to catch, land, and sell less Atlantic herring relative to 2023 conditions. Lower revenues are expected.  Decreases in producer surplus accrue to the Atlantic herring fishing industry.  Decreases in consumer surplus accrue to the users of Atlantic herring, individuals and firms that target American lobster and frequently use herring as bait.   We do not project changes in consumer or producer surplus.  Changes in gross revenues derived from Atlantic herring landings are used as a proxy for these measures.

The rebuilding plan sets lower ABCs, and therefore lower ACLs, in order to rebuild the overfished stock of Atlantic herring to a biomass that can sustain MSY. Furthermore, the stock of Atlantic herring itself has value: it produces future generations of fish and higher stock levels make harvesting less costly. Although not presently available, in the future, a bioeconomic model could be pursued that includes a stock-recruitment relationship to quantify the value of the changes in stock levels. We do not undertake this.

### Management Goals and Objectives

\textcolor{red}{By reference}

### Description of the Fishery and other affected entitites

Annual revenues from herring, deflated to real 2023 dollars using the GDP implicit price deflator are presented in table \ref{tab:herring_rev_table}

```{r herring_rev_table, eval=TRUE}
# ACLs from the GARFo quota monitoring page https://www.greateratlantic.fisheries.noaa.gov/ro/fso/reports/quota_monitoring_archive.html

ACL_mt <- data.frame(year=2019:2024,
                             ACL=c(15574, 12195,5128, 4813, 13287,20141))

yearly_rev<-monthly_util_herring %>%
  select(year, landings_mt, price_mt) %>%
  mutate(herring_value=landings_mt*price_mt)%>%
  group_by(year)%>%
  summarise(herring_value=sum(herring_value,na.rm=TRUE),
            'Landings (mt)'=floor(sum(landings_mt, na.rm=TRUE))
            )%>%
  dplyr::filter(year>=2019)%>%
  left_join(ACL_mt, by=join_by(year==year))%>%
  left_join(deflatorsY, by=join_by(year==year))%>%
  mutate('Herring Value (M)'=((herring_value/fGDPDEF_2023))) %>%
  arrange(year)

# Extract the baseline row (2023)
baseline<-yearly_rev %>%
  dplyr::filter(year==2023)%>%
  select(year, 'Landings (mt)', 'Herring Value (M)') %>%
  rename(Landings='Landings (mt)') %>%
  rename(Actual_Revenue='Herring Value (M)')%>%
  mutate(Actual_Price=Actual_Revenue/Landings) %>%
  mutate(year=as.character(year))
baseline$year<-"Baseline"


yearly_rev<-yearly_rev %>%
  mutate(across(c('Herring Value (M)'), ~ number(.x, accuracy=1000,prefix="$", big.mark=","))) 

yearly_rev<-yearly_rev %>%
  mutate(across(c(`Landings (mt)`, 'ACL'), ~ number(.x, accuracy=1, big.mark=",")))



kbl(yearly_rev %>%
      dplyr::filter(year>=2021 & year<=2023) %>%
    select(c(year, ACL, 'Landings (mt)', 'Herring Value (M)')) , digits=2,booktabs=T, align=c("l",rep('r',times=2)), caption =  "Recent ACLs (metric tons), Landings, and Gross Revenues derived from herring (Real 2023 USD)") %>%
    #column_spec(5:8, width = "2cm")
    kable_styling(full_width = F) %>% 
      row_spec(0,bold=FALSE) 
```

See Sections 3 and 4 for a more complete description of the fishery.


### Statement of the Problem 

The New England Fishery Management Council adopted an ABC control rule in Amendment 8 (A8) to the Atlantic Herring FMP. The ABC control rule prescribes F as a function of SSB. FW8 implemented the ABC control rule for the 2021-2023 fishing years, Framework Adjustment 9 (FW9) implemented the rebuilding plan and the 2023-2025 specifications through a specification action with a SIR.


### Economic impacts relative to the baseline

The 2023 ACL of 13,287mt is used as the baseline. The specifications recommended by the Herring Committee for are 2,710 mt, 6,854 mt, and 6,854 mt in 2025-2027 respectively.  The ABC control rule would set ACLs of 2,710 mt, 6,854 mt, and 11,404 mt in 2025-2027 respectively.  Recent catches have been close to the ACLs, and therefore, this analysis assumes that catch is equal to the ACLs in each of the specification years. This assumption seems reasonable since the draft ACLs are well below recent values.

#### Prices and Revenues

This analysis updates an econometric model, developed in FW9, that estimates a relationship between real 2019 prices and landings, by including additional  years of data and normalizing to real 2023 prices. This allows for a projection of future prices in each of the specification years. Prices are in dollars per metric ton and landings are in thousands of metric tons. The first column of Table 13 contains the model of prices that are used to predict future prices^[A least-squares regression will produce biased estimates if prices and quantities are simultaneously determined.  An Instrumental Variables estimator, where previous year's landings is used as an instrument for landings, can overcome this problem.  A pair of log-transformed models are also estimated. The first column is the preferred specification and used for predictions. The other three columns are presented as robustness checks.   The log-landings coefficient from the IV model is an elasticity and implies that an increase in landings of 1\% will reduce prices by 0.36\%.]. Based on the econometric model of prices, predicted prices and revenues are calculated according to:

\begin{align}
\mbox{Projected Price} &= 894 - 6.079*\mbox{landings}\label{eq:predicted_price}\\
\mbox{Projected Revenue} &=  (894 - 6.079*\mbox{landings}) *\mbox{landings}\label{eq:predicted_landings}
\end{align}

The landings coefficient implies that, on average, a decrease in annual landings of 1,000 mt will increases prices by approximately \$6 per metric ton.  Similarly, an increase in annual landings of 1,000 mt will decrease prices by approximately \$6 per metric ton.

\begin{table}[htbp]
  \begin{center}
    \input{../tables/Yregression_results2023.tex}
     \caption{Econometric model of Atlantic herring prices used to project prices and revenues under the baseline and draft action \label{regression_results}}
  \end{center}
\end{table}

#### Baseline Description

```{r compute_prices_revenues, eval=TRUE}
# 2024 quota is 19141mt

#LandingsCR<-c(23961, 2710, 6854, 11404)

# 2025 to 2027 ACLs
proj_rev<-data.frame(year=2025:2027,
          Landings=c(2710, 6854, 6854)
) 
proj_rev<-proj_rev %>%
  mutate(year=as.character(year))



proj_rev$Actual_Revenue<-NA
proj_rev$Actual_Price<-NA
proj_rev<-rbind(baseline,proj_rev)

proj_rev<-proj_rev %>%
  mutate(Price=894-6.079*Landings/1000) %>%
  mutate(Revenue=Price*Landings) %>%
  rename(Year=year)

#, Landings, Price, Revenue)

# pull in baseline (2023) and bind it here.



assign("baselineRevenue",proj_rev[proj_rev$Year =="Baseline" ,"Revenue"])
baselineRevenue <- as.numeric(baselineRevenue)



proj_rev<-proj_rev %>%
  mutate(Rn=Revenue,
         `Revenue Change`=Revenue-baselineRevenue) %>%
mutate(`Revenue Change` = ifelse(Year == "Baseline", NA, `Revenue Change`))
#  filter(Year %in% c("2025", "2026" ,"2027"))

  

proj_rev<-proj_rev %>%
  mutate(across(c(`Revenue`,'Revenue Change', Actual_Revenue), ~ number(.x, accuracy=1000,prefix="$", big.mark=","))) 

proj_rev<-proj_rev %>%
  mutate(across(c(`Price`, Actual_Price), ~ number(.x, accuracy=1,prefix="$", big.mark=",")))
proj_rev<-proj_rev %>%
  mutate(across(c(`Landings`), ~ number(.x, accuracy=1, big.mark=",")))

baseline2<-proj_rev%>%
  dplyr::filter(Year=="Baseline")


```


The 2023 actual landings of 10,038mt is used as the baseline. The price model projects prices of  **`r baseline2$Price` per metric ton** and real gross revenues derived from Atlantic herring of **`r baseline2$Revenue`**. Both of these figures are higher than the actual prices (**`r baseline2$Actual_Price`**) and revenues (**`r baseline2$Actual_Revenue`** ). On average, predictions from the price model will match the actual prices, but in any particular year, they will be different. Nevertheless, we use the projected prices in the construction of baseline revenue so that an model errors are removed when comparing effects of different sets of ACLs to the baseline.  

#### Benefits (Gross Revenues) of the draft action

```{r prices_revenues_table, eval=TRUE}

proj_rev2 <-proj_rev %>% select(c(Year, Price, Revenue, 'Revenue Change'))
kbl(proj_rev2, digits=0,booktabs=T, align=c("l",rep('r',times=3)), caption =  "Projected landings (mt), prices (real 2023 USD/mt), revenues (real 2023 USD) and revenue change relative to the baseline for 2025-2027 draft specifications") %>%
    #column_spec(5:8, width = "2cm")
    kable_styling(full_width = F) %>% 
      row_spec(0,bold=FALSE) 
```



```{r npv, eval=TRUE}
# Compute NPV of change in revenue at the 3% and 7% discount rates. No table is made here. I'm just computing a pair on numbers and sticking it into the text.
proj_rev$df2<-1.02

proj_rev2<-proj_rev %>%
  filter(Year %in% c("2025", "2026" ,"2027"))%>%
  mutate(Year=as.numeric(Year),
         `Revenue Change`=Rn-baselineRevenue,
         df2=df2^(Year-2025)
         ) %>%
  mutate(rev2=`Revenue Change`/df2) %>%
 summarise(rev2=abs(sum(rev2)),  rc=abs(sum(`Revenue Change`)) ) %>%
  mutate(across(c(rev2, rc), ~ number(.x, accuracy=1000,prefix="$", big.mark=",")))

```

Table \ref{tab:prices_revenues} summarizes the annual prices, revenues, and changes of the draft action relative to the baseline. The draft action will result substantially lower landings relative to the baseline. The decrease in landings results in modestly higher Atlantic herring prices. Overall, the model projects a **decrease in revenues of `r proj_rev2$rc`** over the 2025-2027 time period. When discounted at a 2% discount rate, this corresponds to a net present value **decrease of `r  proj_rev2$rev2`**.

\clearpage

#### Benefits (Gross Revenues) of the ABC Control Rule

```{r prices_revenuesCR, eval=TRUE}
# 2024 quota is 19141mt

proj_revCR<-data.frame(year=2025:2027,
          Landings=c(2710, 6854, 11404)
) 
proj_revCR<-proj_revCR %>%
  mutate(year=as.character(year))



proj_revCR$Actual_Revenue<-NA
proj_revCR$Actual_Price<-NA
proj_revCR<-rbind(baseline,proj_revCR)

proj_revCR<-proj_revCR %>%
  mutate(Price=894-6.079*Landings/1000) %>%
  mutate(Revenue=Price*Landings) %>%
  rename(Year=year)













# 
# 
# Year<-c("Baseline", "2025", "2026", "2027")
# Price<-894-6.079*LandingsCR/1000
# Revenue<-(894-6.079*LandingsCR/1000)*LandingsCR/1000*1000
# proj_revCR<-data.frame(Year, LandingsCR, Price, Revenue)
# names(proj_revCR)[names(proj_revCR) == 'LandingsCR'] <- 'Landings'

assign("baselineRevenue",proj_revCR[proj_revCR$Year =="Baseline" ,"Revenue"])
baselineRevenue2 <- as.numeric(baselineRevenue)



proj_revCR<-proj_revCR %>%
  mutate(Rn=Revenue,
         `Revenue Change`=Revenue-baselineRevenue2) %>%
mutate(`Revenue Change` = ifelse(Year == "Baseline", NA, `Revenue Change`))
#  filter(Year %in% c("2025", "2026" ,"2027"))

proj_revCR<-proj_revCR %>%
  mutate(across(c(`Revenue`, 'Revenue Change'), ~ number(.x, accuracy=1000,prefix="$", big.mark=","))) 

proj_revCR<-proj_revCR %>%
  mutate(across(c(`Price`), ~ number(.x, accuracy=1,prefix="$", big.mark=",")))
proj_revCR<-proj_revCR %>%
  mutate(across(c(`Landings`), ~ number(.x, accuracy=1, big.mark=",")))


proj_revCR2 <-proj_revCR %>% select(c(Year, Price, Revenue, 'Revenue Change'))
kbl(proj_revCR2, digits=0,booktabs=T, align=c("l",rep('r',times=3)), caption =  "Projected landings (mt), prices (real 2023 USD/mt), revenues (real 2023 USD) and revenue change relative to the baseline for 2025-2027 specifications from the Amendment 8 ABC Control Rule.") %>%
    #column_spec(5:8, width = "2cm")
    kable_styling(full_width = F) %>% 
      row_spec(0,bold=FALSE) 
```

```{r npvCR, eval=TRUE}
# Compute NPV of change in revenue at the 2% discount rates. No table is made here. I'm just computing a pair on numbers and sticking it into the text.
proj_revCR$df2<-1.02

proj_revCR2<-proj_revCR %>%
  filter(Year %in% c("2025", "2026" ,"2027"))%>%
  mutate(Year=as.numeric(Year),
         `Revenue Change`=Rn-baselineRevenue2,
         df2=df2^(Year-2025)
         ) %>%
  mutate(rev2=`Revenue Change`/df2) %>%
 summarise(rev2=abs(sum(rev2)), rc=abs(sum(`Revenue Change`)) ) %>%
  mutate(across(c(rev2, rc), ~ number(.x, accuracy=1000,prefix="$", big.mark=",")))

```

Table \ref{tab:prices_revenuesCR} summarizes the annual prices, revenues, and changes of the ABC Control rule ACLs relative to the baseline. These ACLs will result substantially lower landings relative to the baseline.  The decrease in landings results in modestly higher Atlantic herring prices. Overall, the model projects a **decrease in revenues of `r proj_revCR2$rc`** over the 2025-2027 time period. When discounted at a 2% discount rate, this corresponds to a net present value **decrease of `r  proj_revCR2$rev2`**.

Relative to the draft action, the specifications associated with the ABC control rule have higher landings and revenues in 2027.  Because the Atlantic herring ACL is higher in 2027, this is less likely to rebuild the overfished Atlantic herring stock. 



## Regulatory Flexibility Act Analysis

###  A description of the reasons why action by the agency is being considered.
\textcolor{red}{By reference}

### A succinct statement of the objectives of, and legal basis for, the proposed rule.
\textcolor{red}{By reference}

### Number of Small entities


```{r Directly_Regulated_Entities, eval=TRUE}

finalyr<-max(affiliates$year)

affiliates$permit_count<-1

nyears<-length(unique(affiliates$year))

# Recode small_business to a print friendly string (Large, Small). Recode entity_type to nice casing

affiliates<-affiliates %>%
  mutate(entity_type_2023=replace(entity_type_2023, entity_type_2023=="FISHING","Fishing"),
         entity_type_2023=replace(entity_type_2023, entity_type_2023=="FORHIRE","For-Hire"),
         SB_string=case_when(
           small_business==1 ~ "Small",
           small_business==0 ~ "Large")
         ) %>%
    relocate(SB_string, .after=small_business) 

# Make a keyfile that has picks off the one year of data and total herring revenue in the 5 year period.  Get the entity type, small business dummy, the number of herring permits, number of LA herring_permits, and the number of vessels as well. The filter(herring>=1) actually cuts out alot of rows
herring2023<-affiliates %>%
  group_by(affiliate_id) %>%
  summarise(Type=first(entity_type_2023), Size=first(SB_string),
            vessels=sum(permit_count/nyears),
            herringrev=sum(value_161722),
            herring=sum(c_across(starts_with("HRG_"))),
            herringABCE=sum(HRG_A+ HRG_B+HRG_C + HRG_E)
            ) %>%
  filter(herring>=1)

# Compute yearly average revenues, including average revenues by species. Rename the value_permit to value_firm to reflect the change in the column when we do the final summarise
  summary_affiliates<-affiliates %>%
  group_by(affiliate_id,year) %>%
  summarise(across(value_permit:value_914179, sum)) %>%  # Creates a firm-year dataset of values 
    ungroup() %>%
  group_by(affiliate_id) %>%
  summarise(across(value_permit:value_914179, mean)) %>% # Takes the mean of the firm-level dataset of values
    rename(value_firm=value_permit, value_firm_forhire=value_permit_forhire)
            

#merge together they keyfile and the average revenue, keeping just the affiliate_ids that show up in herring2023
Directly_Regulated_Entities<-left_join(herring2023,summary_affiliates,by='affiliate_id')



# Summary of DRE large and small firms in the fishing and for-hire industries. Exclude the inactive (NO_REV).
Directly_Regulated_Entities_table <- Directly_Regulated_Entities %>%
  filter(Type !="NO_REV") %>%
  group_by(Size, Type) %>%
  summarise(Firms=n(),
            Vessels=sum(vessels),
            "Avg Gross Receipts"=round(mean(value_firm),0),
            "Avg Herring Receipts"=round(mean(value_161722),0),
            "25th pct Gross Receipts" = round(quantile(value_firm, probs=.25),0),
            "75th pct Gross Receipts"=round(quantile(value_firm, probs=.75),0)
           ) %>%
  mutate(across(c(`Firms`,`Vessels`), ~ number(.x, big.mark=","))) %>%
  mutate(across(c(`Avg Gross Receipts`,`Avg Herring Receipts`, `25th pct Gross Receipts`, `75th pct Gross Receipts` ), ~ number(.x, accuracy=1000,prefix="$", big.mark=",")))

small_fishing_firms<-Directly_Regulated_Entities_table$Firms[Directly_Regulated_Entities_table$Size=="Small"& Directly_Regulated_Entities_table$Type=="Fishing"]
large_fishing_firms<-Directly_Regulated_Entities_table$Firms[Directly_Regulated_Entities_table$Size=="Large"& Directly_Regulated_Entities_table$Type=="Fishing"]
small_forhire_firms<-Directly_Regulated_Entities_table$Firms[Directly_Regulated_Entities_table$Size=="Small"& Directly_Regulated_Entities_table$Type=="For-Hire"]
```

The directly-regulated entities are the firms that currently hold at least 1 Northeast US herring fishing permit (Categories A, B, C, D, or E).  Firms are classified as "Large" or "Small" based on trailing 5 years of revenue.  Table \ref{tab:make_DRE_table} describes numbers of directly-regulated entities, their main activities, and their revenues from various sources.   `r  small_fishing_firms` small firms derive the majority of their revenue from commercial fishing operations.   `r large_fishing_firms` of the large firms derive the majority of their revenue from commercial fishing activities. 

`r small_forhire_firms` small firms derive a majority of their revenue from for-hire recreational fishing activities. The for-hire firms, while holding at least one Atlantic herring permit, did not derive any revenue from Atlantic herring.

```{r make_DRE_table} 
kbl(Directly_Regulated_Entities_table, digits=0,booktabs=T, align=c("l",rep('r',times=7)), caption =  "Number and characterization of the directly regulated entities and average trailing five years of revenue") %>%
    #column_spec(5:8, width = "2cm")
    kable_styling(full_width = T,latex_options = "hold_position") %>% 
      row_spec(0,bold=FALSE) 
```

Table \ref{tab:make_DRE_table} suggests that there are many small firms in the Atlantic herring industry and that Atlantic herring is minimally important to those firms.  While all of the small fishing firms described in table \ref{tab:make_DRE_table} hold a Atlantic herring permit, many of these firms only hold a category-D open access permit which has a 6,600lb Atlantic herring possession limit. These firms are less impacted by closures of the fishery when the catch limits are reached, because the possession limits are set to 2,000 pounds of Atlantic herring when this occurs. Many of the firms described in Table \ref{tab:make_DRE_table} are not actively engaged in the herring fishery.  The herring fishery has had historically low ACLs since 2018 and some firms have stopped participating in the fishery. They may hold herring permits to preserve the option to fish.

Table \ref{tab:Active_DREs} describes a subset of the directly-regulated small entities, those that are participated in the Atlantic herring fishery between 2019 and 2023 and hold a category A, B, C, or E Atlantic herring permit. Because there are fewer than three active, large firms, we only present a description of the active small firms. The small firms identified in table 16 are the firms most likely to be impacted by the decreases in ACLs in the draft action.



```{r Active_DREs}
# Make a keyfile based on herring2023 that just has firms that landed any herring at any time during the 2019-2023 period.

Active_ABCE<-herring2023 %>%
  filter(herringrev>=1) %>%
  filter(herringABCE>=1)

Active_ABCE<-left_join(Active_ABCE,summary_affiliates,by='affiliate_id')

# Summary of firms active in herring large and small firms in the fishing and for-hire industries.
# Should recode small_business to a print friendly string (Large, Small)
Active_DRE_table <- Active_ABCE %>%
  filter(Type !="NO_REV") %>%
  group_by(Size, Type) %>%
  summarise(Firms=n(),
            Vessels=sum(vessels),
            "Avg Gross Receipts"=round(mean(value_firm),0),
            "Avg Herring Receipts"=round(mean(value_161722),0),
            "25th pct Gross Receipts" = round(quantile(value_firm, probs=.25),0),
            "75th pct Gross Receipts"=round(quantile(value_firm, probs=.75),0)
           ) %>%
  mutate(across(c(`Firms`,`Vessels`), ~ number(.x, big.mark=","))) %>%
  mutate(across(c(`Avg Gross Receipts`,`Avg Herring Receipts`, `25th pct Gross Receipts`, `75th pct Gross Receipts` ), ~ number(.x, accuracy=1000,prefix="$", big.mark=",")))



kbl(Active_DRE_table %>% dplyr::filter(Size=="Small"), digits=0,booktabs=T, align=c("l",rep('r',times=7)), caption =  "Number and characterization of the small, active directly regulated entities with A, B, C, or E permit, trailing five years of data. Figures for the large firms cannot be presented to preserve confidentiality.") %>%
    #column_spec(1:4, width = "1cm") %>%
    kable_styling(full_width = T) %>% 
      row_spec(0,bold=FALSE) 

```


### Impacts on Small firms

```{r projected_revenues}
# Compute the firm-level total revenues and shares.
deflated_affiliates<-affiliates %>%
   select(c(affiliate_id,year, value_permit, value_161722)) %>%
   inner_join(deflatorsY, by=c("year"="year")) %>%
   mutate(value_permit=value_permit/fGDPDEF_2023,
          value_161722=value_161722/fGDPDEF_2023) %>%
   group_by(affiliate_id) %>%
  summarise(across(value_permit:value_161722, sum)) %>%  #  Compute the firm-level gross receipts and herring receipts, totaled over the five years.
  rename(value_firm=value_permit) %>%
  ungroup() %>%
  mutate(th=sum(value_161722)) %>% #compute total herring landed
  mutate(herring_share=value_161722/th, #compute the herring share for each firm
         value_other=value_firm-value_161722) %>% #value of non-herring %>%
  mutate(value_firm=value_firm/nyears,
         value_other=value_other/nyears,
         value_161722=value_161722/nyears) %>% #compute the average annual revenues, non-herring revenues, and herring revenue
  select(c(affiliate_id, value_firm,value_other, herring_share, value_161722))


# Join the projected revenues. 
deflated_affiliates$jc<-1
proj_rev$jc<-1

projected_firm_rev<-full_join(deflated_affiliates,proj_rev, by = "jc", relationship="many-to-many") %>%
                 select(-jc) %>%
  mutate(sim_value_161722=herring_share*Rn) %>%
  mutate(sim_value_firm=value_other+sim_value_161722) %>%
  dplyr::select(-c(Landings, Price, Revenue))

#ensure that the total herring revenues are allocated properly
# this should equal the revenue in "proj_rev"
test1<-projected_firm_rev %>%
  group_by(Year) %>%
  summarise(therring=sum(sim_value_161722))

#Just the firms with herring revenue and at least 1 ABCE permit.
projected_firm_rev_ABCE<-herring2023 %>%
  filter(herringABCE>=1) %>%
  filter(herringrev>=1)

projected_firm_rev_ABCE<-left_join(projected_firm_rev_ABCE,projected_firm_rev,by='affiliate_id') %>%
  dplyr::select(c(affiliate_id, Year, Type, Size, value_firm, value_other,value_161722, sim_value_161722, sim_value_firm ))

# 
# test2<-projected_firm_rev_ABCE %>%
#   group_by(Year) %>%
#   summarise(proj_herring=sum(sim_value_161722),
#             historical_herring=sum(value_161722))



#Baseline revenues
baseline_ABCE <- projected_firm_rev_ABCE %>%
  group_by(Size, Type, Year) %>%
  filter(Type !="NO_REV"  & Year=="Baseline") %>%
  summarise("Baseline Gross Receipts"=round(mean(sim_value_firm),0),
            "Baseline Herring Receipts"=round(mean(sim_value_161722),0)) %>%
  mutate(across(c(`Baseline Gross Receipts`,`Baseline Herring Receipts`), ~ number(.x, accuracy=1000,prefix="$", big.mark=","))) %>%
  select(-Year) %>%
  ungroup


projected_firm_rev_ABCE_table <- projected_firm_rev_ABCE %>%
  group_by(Size, Type, Year) %>%
  filter(Type !="NO_REV" &  Year!="Baseline") %>%
  summarise(Firms=n(),
            "Projected Gross Receipts"=round(mean(sim_value_firm),0),
            "Projected Herring Receipts"=round(mean(sim_value_161722),0)) %>%
  mutate(across(c(`Firms`), ~ number(.x, big.mark=","))) %>%
  mutate(across(c(`Projected Gross Receipts`, `Projected Herring Receipts` ), ~ number(.x, accuracy=1000,prefix="$", big.mark=",")))

projected_firm_rev_ABCE_table<-full_join(projected_firm_rev_ABCE_table,baseline_ABCE, by=c("Size","Type"))


# Inspect projected_firm_rev_ABCE_table to check the number of Large firms.

kbl(projected_firm_rev_ABCE_table %>%dplyr::filter(Size=="Small"), digits=0,booktabs=T, align=c("l",rep('r',times=7)), caption =  "Average projected and baseline gross receipts and herring receipts for small firms with A,B,C, or E permits. Figures for large firms cannot be shown due to data confidentiality.") %>%
   # column_spec(1:4, width = "1.5cm") %>%
    kable_styling(full_width = T) %>%
   # kable_styling(font_size = 8) %>%

      row_spec(0,bold=FALSE) 


```

```{r boxplotsR, fig.cap="\\label{figure_boxR}Box Plots of Projected Firm Level Revenue under the draft action, small firms only"}
projected_firm_rev_ABCE<-projected_firm_rev_ABCE %>%
    filter(Type !="NO_REV" & Size=="Small") #%>%
#   mutate(sort=if_else(Year=="Status Quo", "-1", Year)) %>%
#  arrange(sort) %>%
#  select(-sort)

p<-ggplot(projected_firm_rev_ABCE, aes(Year, sim_value_firm/1000))
p+geom_boxplot(outlier.shape = NA) +
  labs(x="Year", y="Projected Revenue ('000s of Real2023USD)")+
  scale_y_continuous(limits = c(0, 4000) )
```


```{r boxplots_H,  fig.cap="\\label{fig:figure_boxH}Box Plots of Projected Firm Level Herring Revenue under the draft action, small firms only"}
p2<-ggplot(projected_firm_rev_ABCE, aes(Year, sim_value_161722/1000))
p2+geom_boxplot(outlier.shape = NA) +
  labs(x="Year", y="Projected Herring Revenue ('000s of Real2023USD)")+
  scale_y_continuous(limits = c(0, 200) )
```

To describe the effects of the changes in catch limits on small firms, this analysis projects firm-level revenue corresponding to the 2025-2027 ACLs in the draft action. The analysis assumes: 1)  that the share of Atlantic herring landings for each firm is equal to their 2019-2023 average and 2) that the firms non-herring revenues are constant. Directly regulated entities that were inactive therefore have no projected revenue. The focus is on the vessels that have A, B, C, or E permits. Table \ref{tab:projected_revenues} summarizes the projected gross receipts, projected herring receipts, and baseline values.  Figures  \ref{figure_boxR} and \ref{fig:figure_boxH} illustrate the projected yearly distribution of total and herring revenues from the active vessels with A,B,C, or E Atlantic herring permits.

The projected decrease in gross revenues and Atlantic herring revenues is moderate.  In 2025, average gross receipts are projected to fall by over 10% and Atlantic herring receipts are projected to fall by over 70%. Firms may continue exit the Atlantic herring fishery, although this exit may be temporary if stock levels and ACLs increase quickly. The next management track stock assessment is in 2026. Results from that assessment would inform development of the 2027-2029 specifications, and therefore 2027 ACL is likely to be revised based on this stock assessment.

### Compliance Requirements
\textcolor{red}{A description of the projected reporting, record-keeping, and other compliance requirements of the proposed rule, including an estimate of the classes of small entities which will be subject to the requirements of the report or record.}

### Duplications
\textcolor{red}{An identification, to the extent practicable, of all relevant Federal rules, which may duplicate, overlap, or conflict with the proposed rule.}


\newpage



