---
title: "Cost Recovery Impacts"
author: "Min-Yang Lee"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    number_sections: yes
  html_document:
    df_print: paged
  word_document: default
header-includes: \usepackage{setspace}\doublespacing 
urlcolor: blue
editor_options:
  chunk_output_type: console
fontsize: 12pt
---

# Summary and Housekeeping
The Greater Atlantic Regional Fisheries Office is considering changes to the cost recovery programs for catch share fisheries in the region. These updates are intended to simplify regulations and reduce costs for the Scallop Individual Fishing Quota, Tilefish Individual Fishing Quota, and Surfclam and Ocean Quahog Individual Transferable Quota fisheries. This action would result in improved administration and management of the scallop, tilefish, and surfclam and ocean quahog fisheries.

This analysis was written in RMarkdown. It can be found at https://github.com/NEFSC/READ-SSB-Lee-regulatory-analyses

\clearpage

 <!---- 
 The global_options chunk loads libraries, sets options, figures out if you're on a desktop or server, sets years, and sets graphing options
 --->
```{r global_options, include=FALSE}
library("here")
library("tidyverse")
library("scales")
library("knitr")
library("kableExtra")
library("haven")
library("ROracle")
library("purrr")
library("conflicted")
library("glue")
conflicts_prefer(dplyr::filter)
here::i_am("writing/Cost_Recovery_2025_Impacts.Rmd")
options(scipen=999)
#############################################################################
#knitr options

knitr::opts_chunk$set(echo=FALSE, warning = FALSE, error = FALSE, message = FALSE, comment = FALSE, cache = FALSE, progress = TRUE, verbose = FALSE, 
											dpi = 600)
options(tinytex.verbose = TRUE)
# options(knitr.table.format = "latex")
#############################################################################


# RFA data
RFA_filepath<-file.path("//nefscdata","RFA_EO12866_Guidelines" ,"Ownership Data", "current data and metadata","affiliates_2024_06_01.Rdata")




# DeflatorsY, which are pulled by stata
# DeflatorsQ, which are pulled by stata

deflatorsY_path<-here("data_folder","external" ,"deflatorsY.dta")
deflatorsQ_path<-here("data_folder","external" ,"deflatorsQ.dta")


# SC 
sc_filepath<-here("data_folder","external" ,"2024sc_allocation.csv")




###################################################################################################
```


```{r Get_Deflators, include=FALSE, eval=TRUE}


#import deflators this with haven.
deflatorsY<-haven::read_dta(file=deflatorsY_path)%>%
  select(year,fGDPDEF_2023) 
deflatorsQ<-haven::read_dta(file=deflatorsQ_path)%>%
  select(dateq,fGDPDEF_2023Q1)

```

```{r load_RFA_data_and_surfclam, include=FALSE}
load(RFA_filepath)
affiliates<-affiliates_2024_06_01
rm(affiliates_2024_06_01)


scoq<-read.csv(sc_filepath)

scoq<-scoq %>%
  mutate(SBA.Code = case_when(
    SBA.Code=="" ~ "11413",  
    SBA.Code=='?' ~ "11413",
    SBA.Code=='11413?' ~ "11413",
    SBA.Code=='424460?' ~ "424460",  
     .default = SBA.Code))   %>%
  mutate(Size.standard.in.millions = case_when(
    SBA.Code=="11413" ~ "$11 million in revenues",
    Size.standard.in.millions=="100 employees?" ~ "100 employees",  
     .default = Size.standard.in.millions)  ) %>%
     mutate(SBA.Classification = case_when(
    SBA.Code=="11413" ~ "Commercial Fishing",
    SBA.Classification=="Commercial Fishing?" ~ "Commercial Fishing",
    SBA.Classification=="Fish and Seafood Merchant Wholesalers?" ~ "Fish and Seafood Merchant Wholesalers",
     .default = SBA.Classification)  )%>%
     mutate(Size = case_when(
    Size=="" ~ "Small",  
    Size=="Unknown" ~ "Small",
    Size=="Atlantic Capes?" ~ "Small",
    Size=="Large -201 to 500 employees" ~ "Large",
     .default = Size)  )


scoq<-scoq %>%
  mutate(SBA.Code = case_when(
    Size=="Sector 92" ~ "Sector 92",  
     .default = SBA.Code))    %>%
  mutate(Size.standard.in.millions = case_when(
    Size=="Sector 92" ~ "N/A",  
     .default = Size.standard.in.millions)  ) %>%
     mutate(SBA.Classification = case_when(
    Size=="Sector 92" ~ "Sector 92",  
     .default = SBA.Classification)  )

```

    




```{r get_paygov, include=FALSE, eval=TRUE}
#Use oracle to connect
drv<-dbDriver("Oracle")
nova_conn<-dbConnect(drv, id, password=novapw, dbname=nefscusers.connect.string)

# Set up the three sql statements to get paygov. I don't think it's necessary to have a glue() around some of these 
# set the role
# get the data
# reset the role to the usual one.
  paygov_role_set_string<-glue("SET ROLE PAYGOV_SECURE_READ_ROLE IDENTIFIED BY {paygovROLE}")
  querystring<-glue("SELECT * FROM NEFSC_GARFO.PAYGOV_V_CRS_DATA")
  reset_role_string<-glue("SET ROLE ALL")
  
  
  
  dbGetQuery(nova_conn, paygov_role_set_string)
  paygov_data<-dbGetQuery(nova_conn, querystring)
  
  
  querystring2<-glue("SELECT * FROM NEFSC_GARFO.AMS_TILEFISH_PERMIT where TILEFISH_YEAR=2024")

tilefish<-dbGetQuery(nova_conn, querystring2)

tilefish<-tilefish %>%
  rename_with(str_to_lower) 


  
  dbGetQuery(nova_conn, reset_role_string)
  
```

```{r get_annual_landings, include=FALSE, eval=TRUE}
# Scallop GC.
# annual trips, permits, landings and value from scallop on gc scallop trips

  scallopGC_querystring<-glue("select year, sum(lndlb) as scallop_landings, sum(value) as scallop_value, count(unique(camsid)) as trips, count(unique(permit)) as permits from cams_land where camsid in (
     select distinct camsid from cams_subtrip where activity_code_1 like '%SES-SCG%' and activity_code_1 NOT LIKE '%SES-SCG-NG%' and year between 2019 and 2023
 ) and itis_tsn=079718
 group by year")

scallopGC_data<-dbGetQuery(nova_conn, scallopGC_querystring)

scallopGC_data<-scallopGC_data %>%
  rename_with(str_to_lower) 

GCREV_querystring<-glue("select year, sum(value) as total_value from cams_land where camsid in (
     select distinct camsid from cams_subtrip where activity_code_1 like '%SES-SCG%' and activity_code_1 NOT LIKE '%SES-SCG-NG%' and year between 2019 and 2023
 ) 
 group by year")

GCREV_data<-dbGetQuery(nova_conn, GCREV_querystring)

GCREV_data<-GCREV_data %>%
  rename_with(str_to_lower) 

scallopGC_data<-scallopGC_data %>%
  left_join(GCREV_data, by=join_by(year==year))

# SCOQ
# annual trips, permits, landings and value from scallop on gc scallop trips

SCOQ_querystring<-glue("select year, sum(lndlb) as landings, sum(value) as value, count(unique(camsid)) as trips, count(unique(permit)) as permits, itis_tsn 
    from cams_land where itis_tsn in (081343, 080944) and year between 2019 and 2023
    group by year, itis_tsn")

SCOQ_data<-dbGetQuery(nova_conn, SCOQ_querystring)
SCOQ_data<-SCOQ_data %>%
  rename_with(str_to_lower) 

```




```{r get_GC_permits, include=FALSE, eval=TRUE}
# Scallop GC.
# permit level scallop landings and value on scallop ifq trips.

scallopGC_querystring<-glue("select year, sum(lndlb) as scallop_landings, sum(value) as scallop_value, permit from cams_land where camsid in (
     select distinct camsid from cams_subtrip where activity_code_1 like '%SES-SCG%' and activity_code_1 NOT LIKE '%SES-SCG-NG%' and year between 2019 and 2023
 ) and itis_tsn=079718
 group by year, permit")

scallopIFQ_active<-dbGetQuery(nova_conn, scallopGC_querystring)

scallopIFQ_active<-scallopIFQ_active %>%
  rename_with(str_to_lower) %>%
  mutate(permit=as.numeric(permit)) %>%
  relocate(permit, year)


scallopMRI_querystring<-glue("SELECT PER_NUM AS PERMIT,
		RIGHT_ID AS MRI,
		FISHERY,
		DATE_ELIGIBLE,
		DATE_CANCELLED,
		AUTH_TYPE,
		ELIG_STATUS
	  FROM NEFSC_GARFO.mqrs_mort_elig_criteria 
	  WHERE FISHERY = 'GENERAL CATEGORY SCALLOP'
      AND (TRUNC(DATE_ELIGIBLE) <= '01-JAN-24'  or DATE_ELIGIBLE IS NULL) 
      AND (TRUNC(DATE_CANCELLED) >= '01-JAN-23'  or DATE_CANCELLED IS NULL)
      AND not (TRUNC(DATE_ELIGIBLE) =  TRUNC(NVL(DATE_CANCELLED,SYSDATE+20000)))
      order by mri, permit")
      

scallopMRI<-dbGetQuery(nova_conn, scallopMRI_querystring)

scallopMRI<-scallopMRI %>%
  rename_with(str_to_lower) %>%
  mutate(permit=as.numeric(permit))

scallopMRI<-scallopMRI %>%
  group_by(mri) %>%
  arrange(mri, date_eligible) %>%
  mutate(nobs=n(),
    rownum=row_number()) %>%
  filter(nobs==rownum) %>%
  mutate(nobs=n()) %>%
    ungroup() 


# table(scallopMRI$nobs)
# 1 row per mri
stopifnot("All rows of df$nobs must equal 1" = all(scallopMRI$nobs == 1))

scallopMRI<-scallopMRI %>%
 select(permit, mri)



```


```{r get_tilefish_permits, include=FALSE, eval=FALS}

tilefish_querystring<-glue("select fishing_year, root_mri, sum(quantity) as quantity, unit  from nefsc_garfo.ams_allocation_tx
 where fmp='TILE' and allocation_type='BASE' and fishing_year>=2019
 group by unit, root_mri, fishing_year
 order by fishing_year, root_mri, unit")

tilefish_allocations<-dbGetQuery(nova_conn, tilefish_querystring)

tilefish_allocations<-tilefish_allocations %>%
  rename_with(str_to_lower) 

# This doesn't work because not all the tilefish landings are in this dataset.
# can't use activity code because VMS is not mandatory. Can't use CAMS, because there is not TILEFISH code.
# tilefish_landings_string<-glue("select l.fishing_year, t.permit_nbr as permit, sum(l.species_amount) as amount, l.species_uom   from nefsc_garfo.ams_trip_landing l, nefsc_garfo.ams_trip t
#     where l.fmp='TILE' and l.das_id=t.das_id 
#     group by l.fishing_year, t.permit_nbr, l.species_uom");
# 
# tilefish_landings<-dbGetQuery(nova_conn, tilefish_landings_string)
# 
# tilefish_landings<-tilefish_landings %>%
#   rename_with(str_to_lower) 

dbDisconnect(nova_conn)
```



```{r munge_tilefish_scallop, include=FALSE, eval=TRUE}
# rbind the to the scallopMRI
# 

tilefish<-tilefish %>%
  select(c(vp_num,allocation_number))%>%
  rename(permit=vp_num) %>%
  rename(mri=allocation_number)

#combined<-rbind(scallopMRI, tilefish)
combined<-rbind(scallopMRI,tilefish)
combined$mark<-1

# make sure I have just 1 row per permit
combined <-combined %>%
  group_by(permit) %>%
  slice(1) %>%
  ungroup()




scal_and_tileFirms<-affiliates %>%
  filter(year==2023) %>%
  left_join(combined, by=join_by(permit==permit)) %>%
  mutate(mark=replace_na(mark,0)) %>%
  group_by(affiliate_id) %>%
    mutate(markin=sum(mark)) %>%
  filter(markin>=1) %>%
  ungroup()
  
# Keep 1 
 scal_and_tileFirms<-scal_and_tileFirms %>%
 group_by(affiliate_id) %>%
  slice(1)%>%
    ungroup()
  


```




<!---
Some notes on the paygov schema
The view has our bills since 2017 when we started using the Department of Treasury’s Central Receivable Services (CRS) to send our bills. Anything prior to that though would only be for scallops and tilefish as surfclams and ocean quahogs didn’t have a cost recovery component prior to us using CRS.

I would also exclude the year 2024 as we are still getting those bills together and there’s only scallops in the view for 2024.


Agency_Master_Debt_ID = the right_id/allocation number plus the year the bill applies to. In 2021 we started to add a prefix to this data element to help us and our finance group to quickly identify which fishery the payment belongs to.

Agency_Debt_Id = the right ID or allocation number for clams.

Agency_Debtor_Id is a combination of the business ID and the right_id/allocation number.


The table, Paygov.CRS_Business_Debtor_Address has a column with Bids  (Business IDs) but it only has data since 2021 so I'm not really sure if that's the table or not.  At least the view (paygov.v_crs_data) has all the right ids and allocation numbers that were billed.  

--->

<!--- Set the figure numbers for the section, subsection, figures, and tables so things are properly numbered


\setcounter{section}{8}
\setcounter{subsection}{11}

\setcounter{figure}{15}
\setcounter{table}{12}
--->


## Regulatory Impact Analysis 

The purpose of Executive Order 12866 (E.O. 12866, 58 FR 51735, October 4, 1993) is to enhance planning and coordination with respect to new and existing regulations. 

This E.O. requires the Office of Management and Budget (OMB) to review regulatory programs that are considered to be “significant.” 
A significant action is any regulatory action that may:

1. Have an annual effect on the economy of $100 million or more; or adversely affect in a material way the economy, a sector of the economy, productivity, competition, jobs, the environment, public health or safety, or State, local, territorial, or tribal governments or communities;

2. Create a serious inconsistency or otherwise interfere with an action taken or planned by another agency;

3. Materially alter the budgetary impact of entitlements, grants, user fees, or loan programs or the rights and obligations of recipients thereof; or

4. Raise legal or policy issues for which centralized review would meaningfully further the President's priorities or the principles set forth in this Executive order, as specifically authorized in a timely manner by the Administrator of OIRA in each case.

In deciding whether and how to regulate, agencies should assess all costs and benefits of available regulatory alternatives. Costs and benefits shall be understood to include both quantifiable measures (to the fullest extent that these can be usefully estimated) and qualitative measures of costs and benefits that are difficult to quantify, but nevertheless essential to consider. 

### Management Goals and Objectives

\textcolor{red}{The goal of the proposed rule is to streamline the administration of the three LAPPs and lower costs to the fishing industry.}


\clearpage

### Description of the Fishery

Active vessels, trips, and annual revenue for the fishery from 2019 to 2023 are presented in tables\ref{tab:GCscallop_summary} to  \ref{tab:OQ_summary}.  We do not summarize the Tilefish fishery: there are few participants and disclosure is likely to be inconsistent with the confidentiality requirements of the Magnuson-Stevens Act.

```{r GCscallop_summary}

scallopGC_data<-scallopGC_data %>%
  set_names(str_replace_all(names(.), "_", " ")) %>%
  set_names(str_to_title(names(.),locale="en")) %>%
  relocate(Year, Permits, Trips, `Scallop Landings`, `Scallop Value`, `Total Value`)  %>%
   mutate(across(c(`Scallop Value`, `Total Value`), ~ number(.x, accuracy=1000,prefix="$", big.mark=","))) %>%
   mutate(across(c(`Scallop Landings`), ~ number(.x, accuracy=1000, big.mark=","))) %>%
   mutate(across(c(`Trips`), ~ number(.x, accuracy=1, big.mark=","))) 

kbl(scallopGC_data  , booktabs=T, align=c("l",rep('r',times=5)), caption =  "Active Permits, Trips, Landings, and Value (nominal) for the Limited Access General Category IFQ Scallop Fishery") %>%
    #column_spec(5:8, width = "2cm")
    kable_styling(full_width = F) %>% 
      row_spec(0,bold=FALSE) 
```

```{r sc_summary}

#Need to split this into 2 tables

SCOQ_data2<-SCOQ_data %>%
  mutate(species=if_else(itis_tsn=="080944", "Surf Clam", "Ocean Quahog")) %>%
  select(-itis_tsn) %>%
    pivot_wider(id_cols= year ,names_from=species, names_glue="{species} {.value}", values_from=c(permits, trips, landings, value), names_sep=" ") %>%
    set_names(str_to_title(names(.),locale="en")) %>%
  relocate(Year, any_of(starts_with("Surf Clam")))

SCOQ_data2<-SCOQ_data2 %>%
   mutate(across(any_of(ends_with("Value")), ~ number(.x, accuracy=1000,prefix="$", big.mark=",")),
          across(any_of(ends_with("Landings")), ~ number(.x, accuracy=1000, big.mark=",")),
          across(any_of(ends_with("Trips")), ~ number(.x, accuracy=1, big.mark=","))
          )

kbl(SCOQ_data2 %>% select(c("Year", any_of(starts_with("Surf Clam"))))  , booktabs=T, align=c("l",rep('r',times=4)), caption =  "Active Permits, Trips, Landings, and Value (nominal) for the Surf Clam Fishery") %>%
    #column_spec(5:8, width = "2cm")
    kable_styling(full_width = F) %>% 
      row_spec(0,bold=FALSE) 
```

```{r OQ_summary}

kbl(SCOQ_data2 %>% select(c("Year", any_of(starts_with("Ocean Quahog"))))  , booktabs=T, align=c("l",rep('r',times=4)), caption =  "Active Permits, Trips, Landings, and Value (nominal) for the Ocean Quahog Fishery") %>%
    #column_spec(5:8, width = "2cm")
    kable_styling(full_width = F) %>% 
      row_spec(0,bold=FALSE) 
```


### Other Affected Entities

NOAA Fisheries and the U.S. Department of Treasury are other affected entities. Both of these federal government entities would be expected to devote less staff time to collecting on bills.  The federal government recovers costs associated with NOAA Fisheries time, but does not recover costs associated with U.S. Department of Treasury labor expenditures. 


### Statement of the Problem 

\textcolor{red}{Doug: Mostly by reference, but please include the following}

In the Surfclam and Ocean Quahog fishery, cost recovery bills are sent to the entity that received an allocation of quota, and are in proportion to amount of used quota.  When entity A leases quota out to entity B, entity A is billed for the cost recovery. The Tilefish cost recovery is similarly administered.

In the LAGC IFQ scallop fishery, cost recovery bills are sent to the entity that used an allocation of quota and are in  proportion to the amount of used quota.   When entity A leases quota out to entity B, entity B is billed for the cost recovery.

<!---The Magnuson-Stevens Fishery Conservation and Management Act (Magnuson-Stevens Act) requires the collection of fees to recover the “actual costs directly related to the management, data collection, and enforcement” of a Limited Access Privilege Program at 16 U.S.C. § 1854(d)(2). Permit holders in the three cost recovery programs must pay an annual cost recovery fee, not to exceed three percent of the ex-vessel value of the fish harvested under the LAPP. Vessel permits cannot be renewed until the previous year’s bill is paid. --->


### Description of Selected Alternatives

No action is the status quo: GARFO continues to send bills firms that are greater than \$10 and the terms of payment continue to vary by fishery.

The proposed rule would streamline the administration of the cost recovery program, lowering the overall costs of managing the catch share program.   The proposed rule would set the minimum bill at \$25, which is the default minimum debt amount that can be collected by the Department of Treasury's Cross-Servicing program.  

The proposed rule would also standardize billing due dates across the fisheries.  This is expected to have minimal impacts on regulated firms. 


### Economic Impacts Relative to the Baseline

The baseline is the status quo. Under the status quo, NOAA Fisheries implements a cost recovery program as required by 16 U.S.C. § 1854(d)(2).   Table \ref{tab:status_quo_costs} summarizes the total recoverable costs of the LAPPs in the Northeast region^[ https://www.fisheries.noaa.gov/new-england-mid-atlantic/commercial-fishing/2023-annual-report-atlantic-sea-scallop-individual.  Doug: I pulled the Tilefish and SCOQ from the reports you sent, but I don't know how to cite them.].

Table \ref{tab:under_25}  summarizes the total number and value of bills that were over \$10 and under \$25.

The proposed rule would reduce the administrative costs of the program. We estimate that one week of NMFS employee labor is spent for every bill that is under the \$25 threshold.  We account for this time at the ZP-3 wage rate, including fringe benefits. This is approximately \$3,000 per bill or \$15,000 per year.  These costs are paid by fishery participants through the cost recovery program.

The proposed rule would impact the Treasury Department; we estimate one day of Treasury department employee per bill. At a similar rate, this is approximately \$600 per bill or \$3,000 per year. These costs are not paid by fishery participants.

The proposed rule would impact fishery participants directly. We estimate half a day of firm labor is required per bill, or $1,500 per year.  Finally, un-collectable bills could results in a firm being unable to renew fishing permits. This would cause business disruptions in subsequent years, we do not attempt to value these disruptions.


```{r cost_savings}
fishery<-rep(16500, times=10)
dr2<-.02
dr7<-.07
discount2<-rep(1+dr2, times=10)
discount7<-rep(1+dr7, times=10)

for (i in 1:length(discount2)){
    discount2[i]<-discount2[i]^i
    discount7[i]<-discount7[i]^i
}

fishery2<-sum(fishery/discount2)
fishery7<-sum(fishery/discount7)

treasury<-rep(3000, times=10)
treasury2<-sum(treasury/discount2)
treasury7<-sum(treasury/discount7)

# Format
fishery2<-number(fishery2, accuracy=1,prefix="$", big.mark=",")
fishery7<-number(fishery7, accuracy=1,prefix="$", big.mark=",")
treasury2<-number(treasury2, accuracy=1,prefix="$", big.mark=",")
treasury7<-number(treasury7, accuracy=1,prefix="$", big.mark=",")


# perpetuity
perp_fishery2<-number(16500/dr2, accuracy=1,prefix="$", big.mark=",")
perp_fishery7<-number(16500/dr7, accuracy=1,prefix="$", big.mark=",")
perp_treasury2<-number(3000/dr2, accuracy=1,prefix="$", big.mark=",")
perp_treasury7<-number(3000/dr7, accuracy=1,prefix="$", big.mark=",")


```

#### Present Value of Impacts 

It is reasonable to expect these impacts would continue indefinitely. Using a 2\% discount rate, the proposed regulation would reduce  industry costs by `r perp_fishery2`.  It would reduce costs to the Treasury Department by `r perp_treasury2`.  

Using a 7\% discount rate, the proposed regulation would reduce industry costs by `r perp_fishery7`.  It would reduce costs to the Treasury Department by `r perp_treasury7`.


#### Present Value of Impacts Over at Ten Year Planning Period

We also provide estimates of cost reductions over a 10 year planning period.  Using a 2\% discount rate, the proposed regulation would reduce industry costs by `r fishery2`.  It would reduce costs to the Treasury Department by `r treasury2`.  

Over a 10 year planning period, using a 7\% discount rate, the proposed regulation would reduce industry costs by `r fishery7`.  It would reduce costs to the Treasury Department by `r treasury7`.


```{r status_quo_costs}

sq_costs <- data.frame(
    Fishery = c("Surfclam", "Ocean Quahog", 
                    "LAGC-IFQ Scallop", "Tilefish"
                ),
    Year = c(2023, 2023, 2023, 2023),
    Cost = c(71267, 63345, 117373, 46872),
    Value=c(28632399, 21731238, 19396367, 5993249),
    Rate = c(0.0025, 0.0029, 0.006051, 0.007820),
    stringsAsFactors = FALSE
)

updated_costs<-sq_costs

sq_costs <-sq_costs %>%
     mutate(across(any_of(starts_with(c("Cost", "Value"))), ~ number(.x, accuracy=1,prefix="$", big.mark=","))
     )      


kbl(sq_costs%>% select(-c(Year)) , booktabs=T, align=c("l",rep('r',times=2)), caption =  " Recoverable Costs of the LAPPs, Gross Revenues, and Actual recovery rate in the Northeast Region in 2023") %>%
    #column_spec(5:8, width = "2cm")
    kable_styling(full_width = F) %>% 
      row_spec(0,bold=FALSE) 
```




```{r annual_expenses, include=FALSE, eval=TRUE}

paygov_data <- paygov_data %>%
  rename_with(str_to_lower) %>%

    mutate(agency_debt_id=case_when(agency_debt_id == '18998' ~ 'C561', #One debt is wrong, although it could be a one of the examples of a problem
                           .default = agency_debt_id)) %>% 
  mutate(rightid=if_else(plan %in% c("SCALLOP","TILEFISH"),agency_debt_id,NA)
        ) %>%
  mutate(anum=if_else(plan %in% c("SURFCLAM OCEANQUAHOG"),agency_debt_id,NA)
  ) %>%
  mutate(fishery=plan) %>%
  mutate(fishery=if_else(str_detect(anum,"C"), "Surf Clam", ""),
         fishery=if_else(str_detect(anum,"Q"), "Ocean Quahog", fishery),
         fishery=if_else(is.na(anum), plan, fishery)
  ) 

paygov_data_working <-paygov_data %>%
  select(c(year, nature_of_debt_2, fishery, referred_master_case_balance, plan, rightid, anum, program_code)) %>%
  rename(balance=referred_master_case_balance) %>%
  filter(year>=2019 & year<=2023)  %>%# don't include 2024, year's not done yet
  mutate(plan=str_to_title(plan), 
         plan=if_else(plan =="Surfclam Oceanquahog","Surfclam and Ocean Quahog",plan), 
         ) %>%
  mutate(fishery=str_to_title(fishery))

recoverable_expenses<-paygov_data_working %>%
  group_by(fishery, year) %>%
  summarise(cost=round(sum(balance))) %>%
  mutate(cost= number(cost, accuracy=1,prefix="$", big.mark=","))  %>%
  ungroup() %>%
      set_names(str_to_title(names(.),locale="en"))  %>%
  pivot_wider(names_from=Fishery, values_from=c(Cost),  names_glue="{Fishery}") 

kbl(recoverable_expenses, booktabs=T, align=c("l",rep('r',times=4)), caption =  "Total cost recovery billing, 2019-2023") %>%
    #column_spec(5:8, width = "2cm")
    kable_styling(full_width = F) %>% 
      row_spec(0,bold=FALSE) 


```


```{r annual_bills, include=FALSE, eval=TRUE}
annual_count<-paygov_data_working %>%
  filter(balance>=10) %>%
  group_by(fishery, year) %>%
  summarise(dollars=round(sum(balance)),
            count=n()
  ) %>%
  ungroup() %>%
  pivot_wider(names_from=fishery, values_from=c(dollars, count), names_sep=" ") %>%
  relocate(year, `count Scallop`, `dollars Scallop`, `count Surf Clam`, `dollars Surf Clam`, `count Ocean Quahog`, `dollars Ocean Quahog`) %>%
  rename(`Scallop bills`=`count Scallop`,
    `Scallop bill value`= `dollars Scallop`,
    `SC bills` = `count Surf Clam`,
    `SC bill value`= `dollars Surf Clam`,
    `OQ bills` = `count Ocean Quahog`,
    `OQ bill value`= `dollars Ocean Quahog`,
    `Tilefish bills` = `count Tilefish`,
    `Tilefish bill value`= `dollars Tilefish` ) 

annual_count<-annual_count %>%
    mutate(across(everything(), ~replace_na(., 0)))


kbl(annual_count  %>%
  mutate(across(c(`SC bill value`, `OQ bill value`,`Tilefish bill value`, `Scallop bill value`), ~ number(.x, accuracy=1,prefix="$", big.mark=","))) , booktabs=T, align=c("l",rep('r',times=6)), caption =  "Total number of bills over 10 and value of those bills.") %>%
    #column_spec(5:8, width = "2cm")
    kable_styling(full_width = F) %>% 
      row_spec(0,bold=FALSE) 


```

```{r under_25}

under25_count<-paygov_data_working %>%
  filter(balance<25 & balance>=10) %>%
  group_by(fishery, year) %>%
  summarise(dollars=round(sum(balance)),
            count=n()
  )%>%
  ungroup() %>%
  pivot_wider(names_from=fishery, values_from=c(dollars, count), names_sep=" ") %>%
  relocate(year, `count Scallop`, `dollars Scallop`, `count Surf Clam`, `dollars Surf Clam`) %>%
  rename(`Scallop bills`=`count Scallop`,
    `Scallop bill value`= `dollars Scallop`,
    `SC bills` = `count Surf Clam`,
    `SC bill value`= `dollars Surf Clam`,
#    `OQ bills` = `count Ocean Quahog`,
#    `OQ bill value`= `dollars Ocean Quahog`,
#    `Tilefish bills` = `count Tilefish`,
#    `Tilefish bill value`= `dollars Tilefish` 
)

under25_count<-under25_count %>%
    mutate(across(everything(), ~replace_na(., 0)))



kbl(under25_count  %>%
  mutate(across(c(`SC bill value`, `Scallop bill value`), ~ number(.x, accuracy=1,prefix="$", big.mark=","))) , booktabs=T, align=c("l",rep('r',times=4)), caption =  "Total number of bills over 10 under 25 dollars and corresponding revenue.  Tilefish and Ocean Quahog did not have bills that met this criteria") %>%
    #column_spec(5:8, width = "2cm")
    kable_styling(full_width = F) %>% 
      row_spec(0,bold=FALSE) 


```
From 2019 to 2023, there have been approximately 5 bills per year and representing \$35 - \$112 in total revenue. This represents foregone receipts to the government under the proposed rule and a reduction in costs to the fishery. On average, the Surfclam and Ocean Quahog fishery has 1 per year and the scallop fishery has just under 4 per year.


<!---
rearrange



--->

## Regulatory Flexibility Act Analysis

###  A description of the reasons why action by the agency is being considered.
\textcolor{red}{By reference}

### A succinct statement of the objectives of, and legal basis for, the proposed rule.
\textcolor{red}{By reference}

### Number of Small entities

The directly regulated entities are the firms that received allocations of Surfclam, 
Ocean Quahog, or Tilefish quota plus the firms that landed scallops in the LAGC-IFQ 
program.

For Surfclam, Ocean Quahog, and Tilefish, cost recovery is billed to the entity
that received an allocation of quota, in proportion to amount of used quota. 
When entity A leases quota out to entity B, entity A is billed for the cost 
recovery associated with the leased quota that is used.  Entity A is directly 
regulated, Entity B is not. For these two fisheries, quota allocations are not tied
directly to fishing vessels.

For LAGC IFQ scallop fishery, cost recovery is billed to the entity that used an
allocation of quota and is in proportion to the amount of used quota. When 
entity A leases quota out to entity B, entity B is billed for the cost recovery.
Entity B is directly regulated, Entity A is not.

Firms that are active in the LAGC-IFQ Scallop and Tilefish fishery are grouped 
together. We cannot join together the allocation and ownership data, therefore we
use active firms as a way to estimate the number of regulated entities.  This may 
overestimate the number of regulated entities, because permits with identical owners
should be treated as a single firm. It may underestimate the number of the total
number of regulated entities since two fisheries bill for cost recovery based on 
the initial quota owner.  For the same reasons, our estimate of small firms may be
incorrect as well.


Table \ref{tab:SCOQ_DRE} summarizes the directly regulated entities in the Surf clam and
Ocean Quahog fisheries.  Most firms with Surfclam or Ocean Quahog allocations 
are Commercial fishing firms. However, some allocations are owned by firms that
are more properly classified as Fish and Seafood Wholesalers, Commercial Banks,
Credit Unions, Trusts, or Public Sector (Sector 92).


```{r SCOQ_DRE}
scoqDRE<-scoq %>%
  group_by(SBA.Code, SBA.Classification, Size, Size.standard.in.millions) %>%
  summarise(`Entity Count`=n()) %>%
  ungroup() %>%
  rename(`SBA Code`=SBA.Code) %>%
  rename(`Size Standard`=Size.standard.in.millions) %>%
  rename(`Industry Name`=SBA.Classification) %>%
  relocate(`SBA Code`, `Industry Name`, `Size Standard`, Size, `Entity Count`) %>%
  select(-c(`SBA Code`))



kbl(scoqDRE, booktabs=T, align=c("l", "l",rep('r',times=2)), caption =  "Directly Regulated Entities in the Surfclam and Ocean Quahog Fisheries") %>%
    #column_spec(5:8, width = "2cm")
    kable_styling(full_width = F) %>% 
      row_spec(0,bold=FALSE) 


```



Table \ref{tab:Directly_Regulated_Entities} summarizes the directly regulated
entities in the Scallop and Tilefish fisheries.  Most firms with Surfclam or
Ocean Quahog allocations are Commercial fishing firms. However, some allocations are owned by firms that
are more properly classified as Fish and Seafood Wholesalers, Commercial Banks,
Credit Unions, Trusts, or Public Sector (Sector 92).


```{r Directly_Regulated_Entities}

scal_and_tileTable <-scal_and_tileFirms %>%
    group_by(entity_type_2023, small_business) %>%
    summarise(affiliate_total=mean(affiliate_total),
              count_permits=mean(count_permits),
              count_firms=n()
    ) %>%
  mutate(entity_type_2023=replace(entity_type_2023, entity_type_2023=="FISHING","Fishing"),
         entity_type_2023=replace(entity_type_2023, entity_type_2023=="FORHIRE","For-Hire"),
         entity_type_2023=replace(entity_type_2023, entity_type_2023=="NO_REV","Inactive"),
         Size=case_when(
           small_business==1 ~ "Small",
           small_business==0 ~ "Large")
         ) %>%
  rename(`Entity Type`=entity_type_2023) %>%
  rename(`Firm Gross Reciepts`=affiliate_total) %>%
  rename(`Vessels per Firm`=count_permits) %>%
  rename(`Number of Firms`=count_firms) %>%
  relocate(`Entity Type`, Size,`Number of Firms`, `Vessels per Firm`,`Firm Gross Reciepts`) %>%
      mutate(across(c(`Number of Firms`), ~ number(.x, accuracy=1, big.mark=","))) %>%
      mutate(across(c(`Vessels per Firm`), ~ number(.x, accuracy=0.01, big.mark=","))) %>%
      mutate(across(c(`Firm Gross Reciepts`), ~ number(.x, accuracy=1000, big.mark=",", prefix="$")))



kbl(scal_and_tileTable %>%select(-small_business)  , booktabs=T, align=c("l",rep('r',times=5)), caption =  "Directly Regulated Entities in the Tilefish and Scallop Catch Share Fisheries") %>%
    #column_spec(5:8, width = "2cm")
    kable_styling(full_width = F) %>% 
      row_spec(0,bold=FALSE) 


```


### Impacts on Small firms
\textcolor{red}{Need to do. Take yearly changes and compute updated bills.  }

Over the past 5 years, all impacted bills have been in the Scallop or Surfclam fishery. 
We therefore project no impacts to firms in the Tilefish or Ocean Quahog fisheries.

To describe the yearly impacts on small firms, we adjust the recoverable LAPP costs in 2023.  
For firms in the Surfclam fishery, we use the entity size determinations from the most 
recent MAFMC regulatory action.  For the scallop fishery, we use the standard data on 
ownership that links fishing vessels into firms if they fishing vessels have identical
owners.

We then summarize those cost changes for small and large firms in these two fisheries.


```{r num_impacts}

count_impacts<-under25_count %>%
  filter(year==2023)

# there are 4 scallop and 1 surfclam. I'm just going to hard code this.
# count_impacts_longer<-count_impacts %>%
#   pivot_longer(
#     cols = c('Scallop bills', 'Scallop bill value', 'SC bills', 'SC bill value'),
#     names_to = "metric",
#     values_to = "value"
#   ) %>%
#   mutate(fishery=word(metric,1))
  


updated_costs2<-paygov_data_working %>%
  filter(year==2023) %>%
  filter(fishery %in% c("Surf Clam","Scallop"))%>%
  group_by(fishery) %>%
  mutate(total_costs=sum(balance)) %>%
  ungroup() %>%
  mutate(share=balance/total_costs)

# adjust cost

updated_costs2<-updated_costs2 %>%
    mutate(Updated_Cost = case_when(
    fishery=="Surf Clam" ~ total_costs -3000,  
    fishery=="Scallop" ~ total_costs -12000,  
    TRUE ~ total_costs  
  )) %>%
  mutate(tentative_balance=Updated_Cost*share)

#allocate 'forgiven' costs to remainder
updated_costs2<-updated_costs2 %>%
    mutate(tentative_balance2 = case_when(
    tentative_balance<=25 ~ 0,  
    TRUE ~ tentative_balance  
  )) %>%
  group_by(fishery) %>%
  mutate(share2=sum(tentative_balance2)) %>%
  mutate(share2=tentative_balance2/share2) %>%
  mutate(final_updated_balance=share2*Updated_Cost) %>%
  mutate(savings=balance-final_updated_balance) %>%
  ungroup() %>%
  select(c(fishery, balance, anum, rightid, final_updated_balance,savings))


surfclam_costs<-updated_costs2 %>%
  filter(fishery=="Surf Clam") %>%
  full_join(scoq, by=join_by(anum==Alloc.Nbr))

sc_impacts<-surfclam_costs %>%
  filter(is.na(savings)==FALSE) %>%
  group_by(fishery, Size) %>%
  summarise(`Average Savings`=mean(savings),
            `Number of Entities`=n())

    

```

There are 29 small firms in the surfclam fishery that would see average decreases
in annual cost recovery costs of \$52 (Table \ref{tab:surfclam_costs}.  There are 12 large firms that would experience
decreases in annual cost recovery costs of \$86.  Finally, there are 4 "Sector 92" firms that would experience
decreases in annual cost recovery costs of \$117.  


```{r surfclam_costs}

kbl(sc_impacts %>%  select(-fishery) %>%
      mutate(across(c(`Average Savings`), ~ number(.x, accuracy=1, big.mark=",", prefix="$"))) 
, booktabs=T, align=c("l",rep('r',times=2)), caption =  "Average reduction in annual cost share for entities in the surfclam fishery") %>%
    #column_spec(5:8, width = "2cm")
    kable_styling(full_width = F) %>% 
      row_spec(0,bold=FALSE) 

```




```{r scallop_costs }

scallop_costs<-updated_costs2 %>%
  filter(fishery=="Scallop") %>%
  mutate(rightid=as.numeric(rightid)) %>%
  full_join(scallopMRI, by=join_by(rightid==mri)) %>%
  filter(is.na(savings)==FALSE) %>%
  select(c(fishery, balance, rightid, permit, savings))

affiliate_effects<-affiliates %>%
  filter(year==2023)%>%
  select(affiliate_id, small_business, entity_type_2023, permit, affiliate_total) %>%
  left_join(scallop_costs, by=join_by(permit==permit))%>%
  mutate(balance=replace_na(balance,0),
         savings=replace_na(savings, 0))


affiliate_effects<-affiliate_effects %>%
  group_by(fishery, affiliate_id, small_business, entity_type_2023) %>%
  summarise(affiliate_total=first(affiliate_total),
            savings=sum(savings),
            original_cost_recovery=sum(balance))%>%
  filter(original_cost_recovery>0)



scallop_effects<-affiliate_effects %>%
  group_by(fishery, small_business) %>%
  summarise(`Average Savings`=mean(savings),
            `Number of Entities`=n()) %>%
 mutate(Size=case_when(
   small_business==0 ~ "Large",
   small_business==1 ~ "Small"
 )) %>%
  select(c(fishery, Size, `Average Savings`, `Number of Entities`))


```


There are 100 small firms in the scallop fishery;  these firms would experience
decreases in annual cost recovery costs of \$120 (Table \ref{tab:scallop_effects}.  There are two large firms that 
would experience annual decreases of \$13.

```{r scallop_effects}

kbl(scallop_effects %>%  select(-fishery) %>%
      mutate(across(c(`Average Savings`), ~ number(.x, accuracy=1, big.mark=",", prefix="$"))) 
, booktabs=T, align=c("l",rep('r',times=2)), caption =  "Average reduction in annual cost share for entities in the scallop fishery") %>%
    #column_spec(5:8, width = "2cm")
    kable_styling(full_width = F) %>% 
      row_spec(0,bold=FALSE) 

```




### Compliance Requirements
\textcolor{red}{A description of the projected reporting, record-keeping, and other compliance requirements of the proposed rule, including an estimate of the classes of small entities which will be subject to the requirements of the report or record.}

### Duplications
\textcolor{red}{An identification, to the extent practicable, of all relevant Federal rules, which may duplicate, overlap, or conflict with the proposed rule.}


\newpage



