---
title: "Herring state projections"
author: "Min-Yang Lee"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    df_print: paged
    fig_caption: yes
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    number_sections: yes
header-includes: \usepackage{setspace}\doublespacing
urlcolor: blue
editor_options:
  chunk_output_type: console
fontsize: 12pt
---

<!---- 
 The global_options chunk loads libraries, sets options, figures out if you're on a desktop or server, sets years, and sets graphing options
 --->
```{r global_options, include=FALSE}

library("here")
library("ROracle")
library("readr")
 library("foreign")
 library("tidyverse")
 library("scales")
 library("knitr")
 library("lubridate")
 library("kableExtra")
 library("viridis")
library("sf")
library("mapview")
here::i_am("writing/herring_state_projections.Rmd")

#############################################################################
#knitr options

knitr::opts_chunk$set(echo=FALSE, warning = FALSE, error = FALSE, message = FALSE, comment = FALSE, cache = FALSE, progress = TRUE, verbose = FALSE, 
											dpi = 600)
options(tinytex.verbose = TRUE)
# options(knitr.table.format = "latex")
options(scipen=999)

vintage_string<-Sys.Date()
vintage_string<-gsub("-","_",vintage_string)

con <- ROracle::dbConnect(
  drv = ROracle::Oracle(),
  username = id,
  password = novapw,
  dbname = "nefsc_users")


#############################################################################
my_images<-here("images")

descriptive_images<-here("images","descriptive")
exploratory_images<-here("images","exploratory")


# Read in statistical areas
hmas<-here("data_folder","external","Herring_Management_Areas","Herring_Management_Areas.shp")
hmas <- st_read(dsn = hmas)




# ggplot(stat_areas) + 
#   geom_sf() + 
#   geom_sf_text(aes(label = Id), colour = "black") + 
#   coord_quickmap()

# 
# ggplot() + 
#   geom_sf(data=stat_areas)+ 
#   geom_sf_label(aes(label = stat_areas$Id))

```

# Overview -- a map

Here is a quick and dirty map of the herring management areas. 

1A is the inshore Gulf of Maine, which is used by purse seiners in the summer.

1B is the in between area. The quota here has been extremely low in recent years.

2 is Southern New England. It is used by trawlers in the winter. Some of the trawlers specialize. Some of the fishing is by the small mesh fleet out of Rhode Island that also targets squid, mackerel, and butterfish.

3 is the Georges Bank area. This area is used by trawlers and midwater trawlers in the Summer.  Purse seiners cannot effectively fish here.



```{r hmas, include=TRUE}

ggplot(hmas) +
  geom_sf(fill = "#69b3a2", color = "white") + 
  geom_sf_text(aes(label = COMMNAME))
```


# Gross Revenues 

I project gross revenues using the model of prices from Amendment 8 with updated data.  Landings are set equal to the ACLs from the Council Preferred option.  Baseline is the 2023 ACL.  

```{r prices_revenuesCR, eval=TRUE}
# 2024 quota is 19141mt
LandingsCR<-c(23961, 2710, 6854, 6854)

Year<-c("Baseline", "2025", "2026", "2027")
Price<-894-6.079*LandingsCR/1000
Revenue<-(894-6.079*LandingsCR/1000)*LandingsCR/1000*1000
proj_revCR<-data.frame(Year, LandingsCR, Price, Revenue)
names(proj_revCR)[names(proj_revCR) == 'LandingsCR'] <- 'Landings'

assign("baselineRevenue",proj_revCR[proj_revCR$Year =="Baseline" ,"Revenue"])
baselineRevenue2 <- as.numeric(baselineRevenue)



proj_revCR<-proj_revCR %>%
  mutate(Rn=Revenue,
         `Revenue Change`=Revenue-baselineRevenue2) %>%
mutate(`Revenue Change` = ifelse(Year == "Baseline", NA, `Revenue Change`))
#  filter(Year %in% c("2025", "2026" ,"2027"))

proj_revCR2<-proj_revCR %>%
  mutate(across(c(`Revenue`, 'Revenue Change'), ~ number(.x, accuracy=1000,prefix="$", big.mark=","))) 

proj_revCR2<-proj_revCR2 %>%
  mutate(across(c(`Price`), ~ number(.x, accuracy=1,prefix="$", big.mark=",")))
proj_revCR2<-proj_revCR2 %>%
  mutate(across(c(`Landings`), ~ number(.x, accuracy=1, big.mark=",")))


proj_revCR2 <-proj_revCR2 %>% select(-c(Rn))
kbl(proj_revCR2, digits=0,booktabs=T, align=c("l",rep('r',times=3)), caption =  "Projected landings (mt), prices (real 2023 USD/mt), revenues (real 2023 USD) and revenue change relative to the baseline for 2025-2027 specifications from the Amendment 8 ABC Control Rule.") %>%
    #column_spec(5:8, width = "2cm")
    kable_styling(full_width = F) %>% 
      row_spec(0,bold=FALSE) 
```

```{r break_into_hmas, include=TRUE}
# Percentage of the total ACL to each zone
percentages<-data.frame(
  hma=c("1A", "1B", "2", "3"),
  pct=c(0.289,0.043, 0.278, 0.39)
)

hma_rev<-proj_revCR %>%
  select(Year, Landings, Revenue) %>%
  cross_join(percentages)%>%
  mutate(Revenue=Revenue*pct) %>%
  select(Year, Landings, Revenue, hma)

```


```{r get_herring_data, include=TRUE}
# Code to pull get herring data from CAMS 

CURRENT.QUERY = "select cl.year, cl.state, cl.area_herr, sum(nvl(lndlb,0)) as lndlb, sum(nvl(value,0)) as value from cams_land cl
  where cl.year between 2019 and 2023 and cl.itis_tsn=161722 
group by cl.year, cl.state, cl.area_herr"

CAMS_herring<- tbl(con,sql(CURRENT.QUERY)) %>%
    collect() %>%
  rename_with(tolower) %>%
  arrange(year, area_herr, state, lndlb, value)

dbDisconnect(con)

```

# landings, from each area to each state 

There is fishing in 1B, but the total revenues are very low ($15,000 in 2023), so they don't show up well in the bar chart.
```{r plots, include=TRUE}

CAMS_herring2 <- CAMS_herring %>%
  dplyr::filter(!is.na(area_herr)) %>%
  dplyr::filter(state %in% c("MA","CT","ME", "NJ", "RI"))

ggplot(CAMS_herring2
       , aes(y=value, x=area_herr, fill=state)) + 
  facet_wrap(~year) + 
  geom_bar(position="stack", stat="identity")

```


Compute state level percentages for each herring area

```{r state_pcts, include=TRUE}

state_pcts<-CAMS_herring %>%
  dplyr::filter(!is.na(area_herr)) %>%
  group_by(area_herr, state) %>%
  summarise(area_state_value=sum(value)) %>%
  ungroup() %>%
  group_by(area_herr) %>%
  mutate(total_area=sum(area_state_value))%>%
  ungroup()%>%
  mutate(state_share=area_state_value/total_area) %>%
  select(state, area_herr, state_share)%>%
  group_by(area_herr)%>%
  arrange(-state_share, .by_group=TRUE)



kbl(state_pcts, digits=3,booktabs=T, align=c("l",rep('r',times=2)), caption =  "State shares of each HMA, averaged over 2019-2023") %>%
    #column_spec(5:8, width = "2cm")
    kable_styling(full_width = F) %>% 
      row_spec(0,bold=FALSE) 


```



Project state landings for Baseline, 2026, and 2025

```{r state_landings_projections, include=TRUE}

state_rev<-hma_rev %>%
  dplyr::filter(Year %in% c("Baseline","2025","2026")) %>%
  left_join(state_pcts, by=join_by(hma==area_herr), relationship='many-to-many') %>%
  mutate(Revenue=Revenue*state_share)%>%
  group_by(Year,state) %>%
  summarise(Revenue=round(sum(Revenue),0)) %>%
  arrange(desc(Year),desc(Revenue))

write.csv(state_rev, file=here("data_folder","main",paste0("state_rev_",vintage_string,".csv")), row.names=FALSE)

state_rev<-state_rev %>%
  pivot_wider(
    names_from=Year,
    values_from=Revenue,
    names_glue = "Revenue_{Year}",

  )

kbl(state_rev, digits=3,booktabs=T, align=c("l",rep('r',times=3)), caption =  "Projected Revenue by state under Baseline,  2025, and 2026 ACLs") %>%
    #column_spec(5:8, width = "2cm")
    kable_styling(full_width = F) %>% 
      row_spec(0,bold=FALSE) 

```




Compute importance of each herring area to each state. This is a quick way to determine gear: the 1A fishery is Purse Seine, everything else is a mix of Otter trawl and mid-water trawl.

```{r state_hma_usage, include=TRUE}

hma_importance<-CAMS_herring %>%
  dplyr::filter(!is.na(area_herr))  %>%
  dplyr::filter(state %in% c("MA","CT","ME", "NJ", "RI")) %>%
  group_by(area_herr, state) %>%
  summarise(area_state_value=sum(value)) %>%
  ungroup() %>%
  group_by(state) %>%
  mutate(total_state=sum(area_state_value))%>%
  ungroup()%>%
  mutate(hma_importance=area_state_value/total_state) %>%
  select(state, area_herr, hma_importance)%>%
  group_by(state)%>%
  arrange(-hma_importance, .by_group=TRUE)



kbl(hma_importance, digits=3,booktabs=T, align=c("l",rep('r',times=2)), caption =  "Importance of each HMA to each state, averaged over 2019-2023") %>%
    #column_spec(5:8, width = "2cm")
    kable_styling(full_width = F) %>% 
      row_spec(0,bold=FALSE) 


```

  