---
title: "Groundfish Framework 69 --herring and mackerel"
author: "Min-Yang Lee"
date: "10/24/2024"
output:
  pdf_document: default
  html_document: default
urlcolor: blue

---
# Project setup
here(), load libraries, and set a data vintage.  


```{r setup, include=TRUE, echo=TRUE, results=FALSE}
# Set Path
here::i_am("GF69_herring_mackerel/data_wrangle/data_extracting.rmd")
library("here")
library("ROracle")
library("tidyverse")
library("haven")
library("lubridate")
library("readr")

#Data vintage
vintage_string<-Sys.Date()
vintage_string<-gsub("-","_",vintage_string)


START.YEAR = 2020
END.YEAR = 2023

# Set up paths.
herring_haddock_AM_location<-here("input_data","Herring_Haddock_Accountability_Measure_Areas")
```

# Organization


```{r folder_create, include=TRUE, echo=FALSE, results=FALSE}
# You only need to run this once, but nothing bad will happen if you keep include=TRUE.

# Set up some folders

dir.create(here("GF69_herring_mackerel","data"), showWarnings="FALSE")
dir.create(here("GF69_herring_mackerel","data", "intermediate"), showWarnings="FALSE")
dir.create(here("GF69_herring_mackerel","data", "main"), showWarnings="FALSE")

```

# Purpose

This code extracts and processes data, mostly from CAMS_LAND.

*    PERMIT and HULLID (no need to filter by LA or open access herring/mackerel vessels)
*    ITIS_TSN and Species Name (herring and mackerel only)
*    Year (2020-2023)
*    Month
*    Landings (lndlb)
*    Revenue (livlb)
*    Area

# Dependencies

This code depends on:

1.  The ability to connect to NEFSC oracle databases (CAMS).


# Data Overview

Data Comes from CAMS_LAND and CAMS_SUBTRIP. 


# Loading Data fom Oracle 

I'm using DMIS to get the broad stock area (area) and the herring and SMB permits for trips that caught herring or mackerel.

```{r DMIS_Query, echo=TRUE,eval=TRUE}



# Pull in the MRIP_MA_SITE_LIST 
star_dbi_ROracle <- DBI::dbConnect(dbDriver("Oracle"),id, password=novapw, dbname=nefscusers.connect.string)


  CURRENT.QUERY <- paste("select c.* from cams_land c, cams_subtrip t
  where C.ITIS_TSN in (161722,172414)
  and c.year between", START.YEAR, "and",END.YEAR, sep=" ")

CAMS_data<-dplyr::tbl(star_dbi_ROracle,sql(CURRENT.QUERY)) %>%
   collect()


CURRENT.QUERY <- "select * from cams_garfo.cfg_itis"

itis<-dplyr::tbl(star_dbi_ROracle,sql(CURRENT.QUERY)) %>%
   collect()



dbDisconnect(star_dbi_ROracle)
names(CAMS_data) <- tolower(names(CAMS_data))
names(itis) <- tolower(names(itis))

CAMS_data<-CAMS_data %>%
  dplyr::left_join(itis, by=join_by(itis_tsn==itis_tsn), relationship="many-to-one", suffix=c("",".y")) %>%
  select(-ends_with(".y"))



#save to RDS
CAMS_data_name <-paste0("CAMS_data_",vintage_string,".Rds")
saveRDS(CAMS_data, file=here("GF65_herring_mackerel", "data","intermediate",CAMS_data_name))
```


# Tidying up

Send the NAs to zeros and bin into Haddock AM areas.

```{r merge, include=TRUE, echo=TRUE, results=TRUE, eval=TRUE}
#final_product<-dplyr::left_join(APSD.DMIS_WIND_TEST, DMIS_DATA, by = c("DOCID" = "DOCID"))

final_product<-CAMS_data
#Remove NAs from 2 of the value columns. Set them to zero.
final_product<-final_product%>%
    dplyr::mutate(dlr_dollar=ifelse(is.na(value),0,value)
                 
                 )


#assign by Stat area
# 513, 514, 515 -- GOM Area
# 521, 522, 561, 562, 525 GB area


final_product<-final_product %>%
  mutate(area_by_stat=case_when(area %in% c(513,514,515)  ~ "GOM_AREA", .default="NONE"),
  ) %>%
  mutate(area_by_stat=case_when(area %in% c(521,522,561,562,525)  ~ "GB_AREA", .default=area_by_stat),
)





final_DATA_name <-paste0("herring_data",vintage_string)
saveRDS(final_product, file=here("GF69_herring_mackerel", "data","main",paste0(final_DATA_name,".Rds")))
haven::write_sas(data=final_product, path=here("GF69_herring_mackerel", "data","main",paste0(final_DATA_name,".sas7bdat")))

write_delim(final_product, 
            file=here("GF69_herring_mackerel","data","main",paste0(final_DATA_name,".csv")),
            delim=",")






#Summary
final_product_summary <- final_product%>%
  group_by(area_by_stat, calendar_year, itis_tsn, itis_name) %>%
  dplyr::summarise(pounds=sum(livlb), landed=sum(lndlb), revenue=sum(dlr_dollar)) %>%
  ungroup()


summary_name <-paste0("herring_data_summary",vintage_string)
saveRDS(final_product_summary, file=here("GF69_herring_mackerel", "data","main",paste0(summary_name,".Rds")))
haven::write_sas(data=final_product_summary, path=here("GF69_herring_mackerel", "data","main",paste0(summary_name,".sas7bdat")))

write_delim(final_product_summary, 
            file=here("GF69_herring_mackerel","data","main",paste0(summary_name,".csv")),
            delim=",")






```


# R Session Information
```{r session_info, include=TRUE, echo=TRUE, results=TRUE, eval=TRUE}
sessionInfo()
Sys.Date()

```
This may be useful for diagnosing and troubleshooting one day.


